---
title: "Aggrate and compute POMP"
author: "Ruben Arslan"
date: "4/9/2021"
output: 
  html_document:
    toc: yes
    toc_float: yes
    
---


## Load individual datasets
```{r}
##############################################################################################
library(tidyverse)
##alles zu einem Datensatz machen
#alle zusammen gefuegten Rohdaten einlesen

daten1 <- rio::import("Rohdaten_und_einzelne_Datensaetze/Daten_PSK_Stimme_zusammen_roh/daten1.xlsx")
daten2 <- rio::import("Rohdaten_und_einzelne_Datensaetze/Daten_PSK_Stimme_zusammen_roh/daten2.xlsx")
daten3 <- rio::import("Rohdaten_und_einzelne_Datensaetze/Daten_PSK_Stimme_zusammen_roh/daten3.xlsx")
daten4 <- rio::import("Rohdaten_und_einzelne_Datensaetze/Daten_PSK_Stimme_zusammen_roh/daten4.xlsx")
daten5 <- rio::import("Rohdaten_und_einzelne_Datensaetze/Daten_PSK_Stimme_zusammen_roh/daten5.xlsx")
daten6 <- rio::import("Rohdaten_und_einzelne_Datensaetze/Daten_PSK_Stimme_zusammen_roh/daten6.xlsx")
daten7 <- rio::import("Rohdaten_und_einzelne_Datensaetze/Daten_PSK_Stimme_zusammen_roh/daten7.xlsx")
daten8 <- rio::import("Rohdaten_und_einzelne_Datensaetze/Daten_PSK_Stimme_zusammen_roh/daten8.xlsx")
daten9 <- rio::import("Rohdaten_und_einzelne_Datensaetze/Daten_PSK_Stimme_zusammen_roh/daten9.xlsx")
daten10 <- rio::import("Rohdaten_und_einzelne_Datensaetze/Daten_PSK_Stimme_zusammen_roh/daten10_new.xlsx")
daten11 <- rio::import("Rohdaten_und_einzelne_Datensaetze/Daten_PSK_Stimme_zusammen_roh/daten11.xlsx")

data_complete_all_raw <- rbind(daten1, daten2, daten3, daten4, daten5, daten6, daten7, daten8, daten9, daten10, daten11)
```

## Export raw
```{r}
rio::export(data_complete_all_raw, "data_complete_untrans.rds")
```

## Compute POMP (percentage of maximum possible)
### Add min/max for each scale
```{r}
############################################################################################
#Persoenlichkeitsdaten alle auf -2 bis +2 bringen (wie von Ruben empfohlen)
#Formel: (x-5)/10*5  fuer 9er Skala. Sonst immer die 9 austauschen durch Länge der Skala und die erste 5 in der Klammer durch den Skalenmittelpunkt

#Daten1: SOIR 1-5
psych::describe(daten1)
names(daten1)

daten1$soi_minp <- 1
daten1$soi_maxp <- 5

##################################################################
#Daten2: SOIR 1-5
#dominance auch 1-5?
#BFI auch 1-5
psych::describe(daten2)

daten2$soi_minp <- 1
daten2$soi_maxp <- 5
daten2$dominance_minp <- 1
daten2$dominance_maxp <- 5
daten2$big5_minp <- 1
daten2$big5_maxp <- 5


##################################################################
#Daten3: SOIR 1-5
#dominance -3 bis +3?
n_distinct(daten3$dominance)
items <- 8
all(round(daten3$dominance*items) == daten3$dominance*items,na.rm=T)
# 8 items. closest whole digit to min/max is -3/3
#BFI auch 1-5
psych::describe(daten3)

daten3$soi_minp <- 1
daten3$soi_maxp <- 9
daten3$dominance_minp <- -3
daten3$dominance_maxp <- 3
daten3$big5_minp <- 1
daten3$big5_maxp <- 5



# turn sum scores into means
daten3$neuro <- daten3$neuro/7
daten3$extra <- daten3$extra/8
daten3$openn <- daten3$openn/10
daten3$agree <- daten3$agree/8
daten3$consc <- daten3$consc/9

psych::describe(daten3)[,c("min", "max")]

##################################################################
#Daten4: SOIR 1-5
#BFI auch 1-5
psych::describe(daten4)[,c("min", "max")]

daten4$soi_minp <- 1
daten4$soi_maxp <- 5
daten4$big5_minp <- 1
daten4$big5_maxp <- 5

##################################################################
#Daten5: SOIR 1-5
psych::describe(daten5)[,c("min", "max")]
names(daten5)
daten5$soi_minp <- 1
daten5$soi_maxp <- 9

##################################################################
#Daten6: SOIR 1-5
psych::describe(daten6)[,c("min", "max")]
names(daten6)
daten6$soi_minp <- 1
daten6$soi_maxp <- 9

##################################################################
#Daten7: SOIR 1-9
#BFI auch 1-5
#dominance 1-5
daten7$soi_minp <- 1
daten7$soi_maxp <- 9
daten7$dominance_minp <- 1
daten7$dominance_maxp <- 5
daten7$big5_minp <- 1
daten7$big5_maxp <- 5
psych::describe(daten7)

################
##################################################################
#Daten8: SOIR 1-5
#BFI auch 1-5
#dominance -2:2
daten8$soi_minp <- 1
daten8$soi_maxp <- 9
daten8$dominance_minp <- -2
daten8$dominance_maxp <- 2
daten8$big5_minp <- 1
daten8$big5_maxp <- 5

psych::describe(daten8)


###############
##################################################################
#Daten9:
#BFI auch 1-7

psych::describe(daten9 %>% select(extra, consc, neuro, agree,openn))

daten9$big5_minp <- 0
daten9$big5_maxp <- 7


##################################################################
#Daten10:
#BFI auch 1-5

psych::describe(daten10)
daten10$big5_minp <- 1
daten10$big5_maxp <- 5


##################################################################
#Daten11: SOIR 1-9

psych::describe(daten11)
names(daten11)

daten11$soi_minp <- 1
daten11$soi_maxp <- 9
```

### Test that all values are between min/max
```{r}

##############################################################################################
#erneut alles zusammen fuegen um zu z-transformieren

data_complete_all <- list(daten1, daten2, daten3, daten4, daten5, daten6, daten7, daten8, daten9, daten10, daten11) %>% map(~ mutate(., ID = as.character(ID))) %>% bind_rows() %>% as_tibble()

outside_range <- function(vec, min, max) {
   vec < min | vec > max
}
none <- function(df) {
  nrow(df) == 0
}
data_complete_all %>% filter(
  outside_range(extra, big5_minp, big5_maxp)
) %>% none() %>% 
  testthat::expect_true()
data_complete_all %>% filter(
  outside_range(agree, big5_minp, big5_maxp)
) %>% none() %>% 
  testthat::expect_true()
data_complete_all %>% filter(
  outside_range(neuro, big5_minp, big5_maxp)
) %>% none() %>% 
  testthat::expect_true()
data_complete_all %>% filter(
  outside_range(openn, big5_minp, big5_maxp)
) %>% none() %>% 
  testthat::expect_true()
data_complete_all %>% filter(
  outside_range(consc, big5_minp, big5_maxp)
) %>% none() %>% 
  testthat::expect_true()
data_complete_all %>% filter(
  outside_range(behavior, soi_minp, soi_maxp)
) %>% none() %>% 
  testthat::expect_true()
data_complete_all %>% filter(
  outside_range(attitude, soi_minp, soi_maxp)
) %>% none() %>% 
  testthat::expect_true()
data_complete_all %>% filter(
  outside_range(desire, soi_minp, soi_maxp)
) %>% none() %>% 
  testthat::expect_true()
data_complete_all %>% filter(
  outside_range(soir_full, soi_minp, soi_maxp)
) %>% none() %>% 
  testthat::expect_true()

data_complete_all %>% filter(
  outside_range(dominance, dominance_minp, dominance_maxp)
) %>% none() %>% 
  testthat::expect_true()
```

### Use min/max to compute POMP
```{r}
pomp <- function(raw, min, max) {
    (raw - min)/(max-min)
}

data_complete_all <- data_complete_all %>%
  mutate_at(vars(extra, agree, neuro, openn, consc), ~ pomp(., big5_minp, big5_maxp)) %>% 
  mutate_at(vars(behavior, attitude, desire, soir_full), ~ pomp(., soi_minp, soi_maxp)) %>% 
  mutate_at(vars(dominance), ~ pomp(., dominance_minp, dominance_maxp))

data_complete_all %>% select(extra, agree, neuro, openn, consc, behavior, attitude, desire, soir_full, dominance) %>% gather(variable, value) %>% 
  ggplot(aes(value)) + geom_histogram() + facet_wrap(~ variable)
```

## Calculate pf
```{r}
#Pf bilden
data_complete_all$pf <- (scale(data_complete_all$f1)[,1] +
  scale(data_complete_all$f2)[,1] +
  scale(data_complete_all$f3)[,1] +
  scale(data_complete_all$f4)[,1])/4
```

## Add labels
```{r}
library(labelled)
var_label(data_complete_all$dominance) <- "Dominance"
var_label(data_complete_all$neuro) <- "Neuroticism"
var_label(data_complete_all$agree) <- "Agreeableness"
var_label(data_complete_all$extra) <- "Extraversion"
var_label(data_complete_all$openn) <- "Openness"
var_label(data_complete_all$consc) <- "Conscientiousness"
var_label(data_complete_all$soir_full) <- "Unrestricted sociosexuality"
var_label(data_complete_all$f0) <- "Voice pitch"
var_label(data_complete_all$pf) <- "Formants"
data_complete_all$sex_c <- data_complete_all$sex
data_complete_all$sex <- factor(if_else(data_complete_all$sex == 1, "male", "female"))
contrasts(data_complete_all$sex) <- contr.helmert(2)
var_label(data_complete_all$age) <- "Age"
```


### Save pre-standardisation
```{r}
data_complete_all_unstd <- data_complete_all
rio::export(data_complete_all_unstd, "data_complete_2021_unstd_pomp.rds")
```


## Compute z-scores
```{r}
data_complete_all <- data_complete_all %>% mutate_at(vars(extra, agree, neuro, openn, consc, behavior, attitude, desire, soir_full, dominance, f0, f1, f2, f3, f4, pf), ~ scale(.)[,1])

data_complete_all %>% select(extra, agree, neuro, openn, consc, behavior, attitude, desire, soir_full, dominance, f0, f1, f2, f3, f4, pf) %>% gather(variable, value) %>% 
  ggplot(aes(value)) + geom_histogram() + facet_wrap(~ variable)
```

### Save data
```{r}
rio::export(data_complete_all, "data_complete_2021_zscored.rds")
```


## Standardize within dataset, re-add sex differences

```{r}
vcs <- data_complete_all_unstd
vcs <- vcs %>% mutate_at(vars(extra, agree, neuro, openn, consc, behavior, attitude, desire, soir_full, dominance), ~ scale(.)[,1])

# vcs10c <- rio::import("daten10_formants.rds")
# vcs10 <- vcs %>% filter(dataset == 10)
# vcs10 <- vcs10 %>% select(-(f0:f4)) %>% left_join(vcs10c)
# vcs <- vcs %>% filter(dataset != 10) %>% 
#   bind_rows(vcs10)
```

i) we first standardise within datasets
```{r}
svcs <- vcs %>% group_by(dataset) %>% 
  mutate(f0 = scale(f0)[,1],
         f1 = scale(f1)[,1],
         f2 = scale(f2)[,1],
         f3 = scale(f3)[,1],
         f4 = scale(f4)[,1])
```

ii) we use the HQ datasets with both genders to estimate mean diff of m/f and restricted variance

```{r}
svcs %>% filter(dataset %in% c(2,3, 5, 9)) %>% ungroup() %>% 
  summarise_at(vars(f0:f4), ~broom::tidy(t.test(. ~ sex))$estimate)

svcs %>% filter(dataset %in% c(2,3, 5, 9)) %>% 
  group_by(dataset) %>% 
  summarise_at(vars(f0:f4), ~broom::tidy(t.test(. ~ sex))$estimate)

svcs %>% filter(dataset %in% c(2,3, 5, 9)) %>% 
  group_by(dataset, sex) %>% 
  summarise_at(vars(f0:f4), list(mean = ~mean(., na.rm = T), sd = ~sd(., na.rm = T)))
# not that much variation in sex diff across datasets, so we pool

sex_diffs <- svcs %>% filter(dataset %in% c(2,3, 5, 9)) %>% 
  group_by(sex) %>% 
  summarise_at(vars(f0:f4), list(mean = ~mean(., na.rm = T), sd = ~sd(., na.rm = T)))
sex_diffs
```

iii) we fudge the data in the single gender datasets `((x + gender_mean) * sd_gender)`

```{r}
svcs %>% filter(!dataset %in% c(2,3, 5, 9)) %>% 
  group_by(dataset, sex) %>% 
  summarise_at(vars(f0:f4), list(mean = ~mean(., na.rm = T), sd = ~sd(., na.rm = T)))

svcs <- svcs %>% 
  left_join(sex_diffs, by = "sex") %>% 
  mutate(f0 = if_else(!dataset %in% c(2,3, 5, 9),
                      f0 * f0_sd + f0_mean, f0),
         f1 = if_else(!dataset %in% c(2,3, 5, 9),
                      f1 * f1_sd + f1_mean, f1),
         f2 = if_else(!dataset %in% c(2,3, 5, 9),
                      f2 * f2_sd + f2_mean, f2),
         f3 = if_else(!dataset %in% c(2,3, 5, 9),
                      f3 * f3_sd + f3_mean, f3),
         f4 = if_else(!dataset %in% c(2,3, 5, 9),
                      f4 * f4_sd + f4_mean, f4))

svcs %>% filter(!dataset %in% c(2,3, 5, 9)) %>% 
  group_by(dataset, sex) %>% 
  summarise_at(vars(f0:f4), list(mean = ~mean(., na.rm = T), sd = ~sd(., na.rm = T)))

svcs %>% filter(!dataset %in% c(2,3, 5, 9)) %>% ungroup() %>% 
  summarise_at(vars(f0:f4), ~broom::tidy(t.test(. ~ sex))$estimate)
svcs %>% filter(dataset %in% c(2,3, 5, 9)) %>% ungroup() %>% 
  summarise_at(vars(f0:f4), ~broom::tidy(t.test(. ~ sex))$estimate)
```

iv) then we average across f1 to f4 and standardise pf again
```{r}
svcs %>% ungroup() %>% 
  summarise_at(vars(f0:f4), list(mean = ~mean(., na.rm = T), sd = ~sd(., na.rm = T)))

svcs <- svcs %>% mutate(pf = scale(f1 + f2 + f3 + f4)[,1])
```


v) let's check intercorrelations in each dataset after this transformation

```{r}
vcs %>% select(dataset, f0:f4, sex_c) %>%
  group_by(dataset) %>% 
  mutate_at(vars(f0:f4),  ~resid(lm(. ~ sex_c, na.action = na.exclude))) %>% 
  summarise(corrr::correlate(across(f0:f4)) %>% corrr::shave() %>% corrr::stretch()) %>% 
  unite(vars, x, y) %>% 
  drop_na() %>% 
  ggplot(aes(dataset, r)) +
  geom_text(aes(label = dataset)) + 
  coord_flip() +
  facet_wrap(~ vars)

svcs %>% select(dataset, f0:f4, sex_c) %>% 
  group_by(dataset) %>% 
  mutate_at(vars(f0:f4),  ~resid(lm(. ~ sex_c, na.action = na.exclude))) %>% 
  summarise(corrr::correlate(across(f0:f4)) %>% corrr::shave() %>% corrr::stretch()) %>% 
  unite(vars, x, y) %>% 
  drop_na() %>% 
  ggplot(aes(dataset, r)) +
  geom_text(aes(label = dataset)) + 
  coord_flip() +
  facet_wrap(~ vars)

bind_rows(stdised = svcs %>% select(dataset, f0:f4, sex_c) %>% 
  ungroup() %>% 
  mutate_at(vars(f0:f4),  ~resid(lm(. ~ sex_c, na.action = na.exclude))) %>% 
  summarise(corrr::correlate(across(f0:f4)) %>% corrr::shave() %>% corrr::stretch()) %>% 
  unite(vars, x, y) %>% 
  drop_na(),
  
  unstdised = vcs %>% select(dataset, f0:f4, sex_c) %>%
  ungroup() %>% 
  mutate_at(vars(f0:f4),  ~resid(lm(. ~ sex_c, na.action = na.exclude))) %>% 
  summarise(corrr::correlate(across(f0:f4)) %>% corrr::shave() %>% corrr::stretch()) %>% 
  unite(vars, x, y) %>% 
  drop_na(), .id = "process") %>% 
  ggplot(aes(process, r)) +
  geom_text(aes(label = sprintf("%.2f", r))) + 
  coord_flip() +
  facet_wrap(~ vars)
```

vi) let's check how this looks compared to the simple approach
```{r}
svcs <- svcs %>% ungroup()
vcs_2 <- svcs %>% select(voice_id, f0:f4, pf) %>%
  inner_join(
    data_complete_all %>% select(voice_id, f0:f4, pf), by = "voice_id", suffix = c("_within", "_std"))
rcamisc::mtmm(vcs_2 %>% ungroup() %>% select(-voice_id))
```


### Distributions by dataset
```{r}
svcs$sex <- factor(if_else(svcs$sex_c == 1, "male", "female"))
contrasts(svcs$sex) <- contr.helmert(2)

ggplot(svcs, aes(f0, fill = factor(dataset))) + 
  geom_histogram(position = "identity", alpha = 0.4)+
  facet_wrap(~ sex, scales = "free_x") +
  scale_fill_viridis_d()

ggplot(svcs, aes(f1, fill = factor(dataset))) + 
  geom_histogram(position = "identity", alpha = 0.4)+
  facet_wrap(~ sex, scales = "free_x") +
  scale_fill_viridis_d()

ggplot(svcs, aes(f2, fill = factor(dataset))) + 
  geom_histogram(position = "identity", alpha = 0.4)+
  facet_wrap(~ sex, scales = "free_x") +
  scale_fill_viridis_d()

ggplot(svcs, aes(f3, fill = factor(dataset))) + 
  geom_histogram(position = "identity", alpha = 0.4)+
  facet_wrap(~ sex, scales = "free_x") +
  scale_fill_viridis_d()

ggplot(svcs, aes(f4, fill = factor(dataset))) + 
  geom_histogram(position = "identity", alpha = 0.4)+
  facet_wrap(~ sex, scales = "free_x") +
  scale_fill_viridis_d()

ggplot(svcs, aes(pf, fill = factor(dataset))) + 
  geom_histogram(position = "identity", alpha = 0.4)+
  facet_wrap(~ sex, scales = "free_x") +
  scale_fill_viridis_d()
```

### Save data
```{r}
rio::export(svcs, "data_complete_2021_within_zscored.rds")
```


## Outlier removal
```{r}
svcs <- data_complete_all
svcs <- svcs %>%  group_by(sex) %>% 
  mutate(pf_threshold_hi = median(pf, na.rm = T) + 2.5 * mad(pf, na.rm = T),
         pf_threshold_lo = median(pf, na.rm = T) - 2.5 * mad(pf, na.rm = T),
         f0_threshold_hi = median(f0, na.rm = T) + 2.5 * mad(f0, na.rm = T),
         f0_threshold_lo = median(f0, na.rm = T) - 2.5 * mad(f0, na.rm = T))

pf_outliers <- svcs %>% 
  filter(pf < pf_threshold_lo | pf > pf_threshold_hi)
nrow(pf_outliers)
xtabs(~ dataset + sex, pf_outliers)

f0_outliers <- svcs %>% 
  filter(f0 < f0_threshold_lo | f0 > f0_threshold_hi)
nrow(f0_outliers)
xtabs(~ dataset + sex, f0_outliers)

vcs <- svcs %>% filter(
  pf > pf_threshold_lo, 
  pf < pf_threshold_hi, 
  f0 > f0_threshold_lo, 
  f0 < f0_threshold_hi)

psych::describeBy(vcs %>% ungroup() %>% select(sex_c, f0:f4, pf), vcs$dataset)
```

### Save data
```{r}
rio::export(vcs, "data_complete_2021_within_zscored_no_outliers.rds")
```
