---
title: "Preregistered analysis"
author: "Ruben Arslan"
date: "3/5/2019"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: "hide"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=F)
library(tidyverse)
library(knitr)
library(brms)
library(sjPlot)
library(bayestestR)
library(labelled)
library(cowplot)
theme_set(theme_bw())
```

## Load data

```{r}
vcs <- rio::import("data_complete_all_anonym_allZ_unfiltered.xlsx")
var_label(vcs$dominance) <- "Dominance"
var_label(vcs$neuro) <- "Neuroticism"
var_label(vcs$agree) <- "Agreeableness"
var_label(vcs$extra) <- "Extraversion"
var_label(vcs$openn) <- "Openness"
var_label(vcs$consc) <- "Conscientiousness"
var_label(vcs$soi_full) <- "Unrestricted sociosexuality"
var_label(vcs$f0) <- "Voice pitch"
var_label(vcs$pf) <- "Formants"
vcs$sex_c <- vcs$sex
vcs$sex <- factor(if_else(vcs$sex == 1, "male", "female"))
contrasts(vcs$sex) <- contr.helmert(2)
var_label(vcs$sex) <- "Sex"
set.seed(1)
var_label(vcs$age) <- "Age"
vcs <- vcs %>% 
  mutate(
    age = if_else(dataset == 9, 20, age)/10,
    age_se = if_else(dataset == 9, 3, 0.5)/10
  )
vcs <- vcs %>% filter(!is.na(f0), !is.na(pf), !is.na(age))

warmup <- 2000
iter <- warmup + 2000
chains <- 4
control <- list(adapt_delta = 0.99)
priors <- c(
  prior(normal(0, 3), class = b)
)

variable_labels <- c("Intercept"= "Intercept",  "sex1" = "Sex [male]", "bsp_meageage_se" = "Age±SE", "f0" = "Voice pitch (f0)", "pf" = " Formant position (Pf)", "age" = "Age", "f0:sex1" = "Voice pitch (f0) × Sex")
effect_labels <- c("b_Intercept"= "Intercept",  "b_sex1" = "Sex [male]", "bsp_meageage_se" = "Age±SE", "b_f0" = "Voice pitch (f0)", "b_pf" = " Formant position (Pf)", "b_age" = "Age", "b_f0.sex1" = "Voice pitch (f0) × Sex")

```


## Hypothesis 1: Dominance

Participants with lower voice pitch will have a more dominant personality.

__Interpretation:__ The data are are consistent with substantial linear negative relationships
between `f0` and dominance. The 89% HDI for `f0` falls entirely outside the ROPE, but the HDI for `pf` falls almost entirely within it. This evidence is consistent with a non-negligible association, where people with deeper voices are more dominant (after adjusting for age and gender). Further research is needed to verify if the association with `pf` is truly negligible in size.

### Visually diagnose non-linearity
```{r,warning=FALSE}
ggplot(vcs, aes(f0, dominance)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(pf, dominance)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(age*10, dominance)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  scale_x_continuous("Age") +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 
```

__Decisions upon visual diagnosis:__ Visual diagnostic show no clear sign of nonlinearities. 
We will fit linear effects for f0, pf, and age. It is not necessary to model measurement error
in age, as dataset 9 (where age was not noted individually) is not included in these analyses.
Visually, there could be an interaction between sex and f0. 


### Models
```{r}
h1_simple <- brm(dominance ~ f0 + pf + sex + age + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/dominance/h1_simple") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 


h1_after_diagnosis <- brm(dominance ~ f0*sex + pf + sex + age + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, cores = chains, chains = chains,
          prior = priors, 
          control = control, save_mevars = TRUE,
          file = "models/dominance/h1_nonlinear") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 
# conditional_smooths(h1_after_diagnosis)

compare_models <- loo_compare(h1_simple, h1_after_diagnosis)
compare_models

h1_sex_mod_dataset_varying <- brm(dominance ~ f0 + sex + age + 
                                    (1 + f0 + sex || dataset), data = vcs,
          prior = priors,
          iter = iter + 2000, warmup = warmup + 1000, cores = chains, chains = chains,
          control = control, save_mevars = TRUE,
          file = "models/dominance/h1_sex_mod_dataset_varying2") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

h1_after_diagnosis_melsm <- brm(
  bf(dominance ~ f0 + sex + age + (1 | dataset),
     sigma ~ f0 + sex + age + (1 | dataset)), data = vcs,
          prior = priors,
          iter = iter + 2000, warmup = warmup + 1000, cores = chains, chains = chains,
          control = control, save_mevars = TRUE,
          file = "models/dominance/h1_after_diagnosis_melsm") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 
  

compare_models <- loo_compare(h1_simple, h1_after_diagnosis, h1_sex_mod_dataset_varying,
                      h1_after_diagnosis_melsm)
compare_models

r2s <- list(h1_simple=h1_simple, h1_after_diagnosis=h1_after_diagnosis, h1_sex_mod_dataset_varying=h1_sex_mod_dataset_varying,
                      h1_after_diagnosis_melsm=h1_after_diagnosis_melsm) %>% 
  map(~ { x <- as_tibble(bayes_R2(.))
          x$loo_R2 <- loo_R2(.)
          x
          }) %>%
  bind_rows(.id="model") %>% 
  arrange(desc(loo_R2))

sjPlot::tab_model(h1_simple, bpe = "mean",show.ngroups = T,ci.hyphen = ";",
                  pred.labels = variable_labels)
equiv_test <- equivalence_test(h1_simple, range = c(-0.1, 0.1))
equiv_test_table <- equiv_test %>% 
  mutate(Parameter = recode(Parameter, !!!effect_labels)) %>% 
  mutate(
    ROPE_Percentage = sprintf("%2.f%%", 100*ROPE_Percentage),
    HDI = sprintf("[% .2f;% .2f]", HDI_low, HDI_high)) %>% 
  select(Parameter, H0 = ROPE_Equivalence, `inside ROPE` = ROPE_Percentage, `89% HDI` = HDI)
kable(equiv_test_table, caption = "Test whether the 89% highest-density interval (HDI) is fully within the region of practical equivalence (ROPE) of [-0.1;0.1] that we set (where all continuous variables, except age are standardised).")
plot(equiv_test) + scale_y_discrete("Effect", breaks = names(effect_labels), labels = effect_labels)
```

<details><summary>Model details</summary>

```{r}
summary(h1_simple)
summary(h1_after_diagnosis)
conditional_effects(h1_after_diagnosis_melsm)
# conditional_smooths(h1_after_diagnosis)
summary(h1_sex_mod_dataset_varying)
summary(h1_after_diagnosis_melsm)
kable(r2s, caption = "Explained variance, regular and leave-one-out.")
kable(coef(h1_sex_mod_dataset_varying)$dataset[, ,"f0"], caption = "Estimated association between f0 and outcome by dataset")
```

</details>


## Hypothesis 2:  Extraversion

Participants with lower voice pitch will score higher on extraversion

__Interpretation:__ The data are are consistent with a substantial linear negative relationship
between `f0` and extraversion. The 89% HDI for `f0`
excludes and falls entirely outside the ROPE. The 89% of the HDI for `pf` overlaps zero and the ROPE boundaries. This evidence is consistent with an association, where people with deeper voices have higher extraversion (after adjusting for age and gender), but further research is needed to test whether the association with  `pf` is negligible in size.


### Visually diagnose non-linearity
```{r,warning=FALSE}
ggplot(vcs, aes(f0, extra)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour =  "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(pf, extra)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(age*10, extra)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  scale_x_continuous("Age") +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 
```

__Decisions upon visual diagnosis:__ Visual diagnostic shows signs of a potential interaction by sex coupled with nonlinearity for pf.
We will fit separate splines by sex for pf. It is necessary to model measurement error in age, as dataset 9 (where age was not noted individually) is included in these analyses.


### Models
```{r}
h1_simple <- brm(extra ~ f0 + pf + sex + me(age, age_se) + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/extra/h1_simple") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 


h1_after_diagnosis <- brm(extra ~ f0 + s(pf, by = sex) + sex + me(age, age_se) + (1 | dataset), data = vcs,
          iter = iter + 1000, warmup = warmup + 1000, cores = chains, chains = chains,
          prior = priors, 
          control = control, save_mevars = TRUE,
          file = "models/extra/h1_nonlinear2") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

conditional_smooths(h1_after_diagnosis)

compare_models <- loo_compare(h1_simple, h1_after_diagnosis)
compare_models

h1_sex_mod_dataset_varying <- brm(extra ~ f0 + sex + me(age, age_se) + 
                                    (1 + f0 + sex || dataset), data = vcs,
          prior = priors,
          iter = iter + 2000, warmup = warmup + 1000, cores = chains, chains = chains,
          control = control, save_mevars = TRUE,
          file = "models/extra/h1_sex_mod_dataset_varying2") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

h1_after_diagnosis_melsm <- brm(
  bf(extra ~ f0 + sex + me(age, age_se) + (1 | dataset),
     sigma ~ f0 + sex + me(age, age_se) + (1 | dataset)), data = vcs,
          prior = priors,
          iter = iter + 2000, warmup = warmup + 1000, cores = chains, chains = chains,
          control = control, save_mevars = TRUE,
          file = "models/extra/h1_after_diagnosis_melsm") %>%
  add_criterion("loo") %>%
  add_criterion("bayes_R2") %>%
  add_criterion("loo_R2")


compare_models <- loo_compare(h1_simple, h1_after_diagnosis, h1_sex_mod_dataset_varying ,h1_after_diagnosis_melsm
                      )
compare_models
r2s <- list(h1_simple=h1_simple, h1_after_diagnosis=h1_after_diagnosis, h1_sex_mod_dataset_varying=h1_sex_mod_dataset_varying,h1_after_diagnosis_melsm=h1_after_diagnosis_melsm) %>% 
  map(~ { x <- as_tibble(bayes_R2(.))
          x$loo_R2 <- loo_R2(.)
          x
          }) %>%
  bind_rows(.id="model") %>% 
  arrange(desc(loo_R2))

sjPlot::tab_model(h1_simple, bpe = "mean",show.ngroups = T,ci.hyphen = ";",
                  pred.labels = variable_labels)
equiv_test <- equivalence_test(h1_simple, range = c(-0.1, 0.1))
equiv_test_table <- equiv_test %>% 
  mutate(Parameter = recode(Parameter, !!!effect_labels)) %>% 
  mutate(
    ROPE_Percentage = sprintf("%2.f%%", 100*ROPE_Percentage),
    HDI = sprintf("[% .2f;% .2f]", HDI_low, HDI_high)) %>% 
  select(Parameter, H0 = ROPE_Equivalence, `inside ROPE` = ROPE_Percentage, `89% HDI` = HDI)
kable(equiv_test_table, caption = "Test whether the 89% highest-density interval (HDI) is fully within the region of practical equivalence (ROPE) of [-0.1;0.1] that we set (where all continuous variables, except age are standardised).")
plot(equiv_test) + scale_y_discrete("Effect", breaks = names(effect_labels), labels = effect_labels)
```

<details><summary>Model details</summary>

```{r}
summary(h1_simple)
summary(h1_after_diagnosis)
conditional_effects(h1_after_diagnosis_melsm)
# conditional_smooths(h1_after_diagnosis_melsm)
summary(h1_sex_mod_dataset_varying)
summary(h1_after_diagnosis_melsm)
kable(r2s, caption = "Explained variance, regular and leave-one-out.")
kable(coef(h1_sex_mod_dataset_varying)$dataset[, ,"f0"], caption = "Estimated association between f0 and outcome by dataset")
equivalence_test(h1_after_diagnosis_melsm, range = c(-0.1, 0.1))
```

</details>


## Hypothesis 3: Agreeableness

Participants with lower voice pitch will score higher on agreeableness.

__Interpretation:__ The credible intervals for `f0` and `pf` include zero, but the 89% HDI does not fall entirely within the ROPE.  This evidence is consistent with a negligible association between `f0`/`pf` and agreeableness. Further research is needed to verify if the associations are truly negligible in size.


### Visually diagnose non-linearity
```{r,warning=FALSE}
ggplot(vcs, aes(f0, agree)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour =  "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(pf, agree)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(age*10, agree)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  scale_x_continuous("Age") +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 
```

__Decisions upon visual diagnosis:__ Visual diagnostic shows signs of nonlinearity for f0 and pf, but no clear interactions by sex.
We will fit splines for f0, and pf. It is necessary to model measurement error
in age, as dataset 9 (where age was not noted individually) is included in these analyses.


### Models
```{r}
h1_simple <- brm(agree ~ f0 + pf + sex + me(age, age_se) + (1 | dataset), data = vcs,
          iter = iter + 1000, warmup = warmup + 1000, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/agree/h1_simple2") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 



h1_after_diagnosis <- brm(agree ~ f0 * sex + pf + sex + me(age, age_se) + (1 | dataset), data = vcs,
                          iter = iter + 1500, warmup = warmup + 1500, cores = chains, chains = chains,
                          prior = priors, 
                          control = control, save_mevars = TRUE,
                          file = "models/agree/h1_nonlinear4") %>% 
    add_criterion("loo") %>% 
    add_criterion("bayes_R2") %>% 
    add_criterion("loo_R2") 

compare_models <- loo_compare(h1_simple, h1_after_diagnosis)
compare_models

h1_sex_mod_dataset_varying <- brm(agree ~ f0 * sex + sex + me(age, age_se) + 
                                    (1 + f0 + sex || dataset), data = vcs,
          prior = priors,
          iter = iter + 2000, warmup = warmup + 1000, cores = chains, chains = chains,
          control = control, save_mevars = TRUE,
          file = "models/agree/h1_sex_mod_dataset_varying2") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

h1_after_diagnosis_melsm <- brm(
  bf(agree ~ f0 * sex + sex + me(age, age_se) + (1 | dataset),
     sigma ~ f0 * sex + sex + me(age, age_se) + (1 | dataset)), data = vcs,
          prior = priors,
          iter = iter + 2000, warmup = warmup + 1000, cores = chains, chains = chains,
          control = control, save_mevars = TRUE,
          file = "models/agree/h1_after_diagnosis_melsm2") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 
  

compare_models <- loo_compare(h1_simple, h1_after_diagnosis, h1_sex_mod_dataset_varying,
                      h1_after_diagnosis_melsm)
compare_models


r2s <- list(h1_simple=h1_simple, h1_after_diagnosis=h1_after_diagnosis, h1_sex_mod_dataset_varying=h1_sex_mod_dataset_varying,
                      h1_after_diagnosis_melsm=h1_after_diagnosis_melsm) %>% 
  map(~ { x <- as_tibble(bayes_R2(.))
          x$loo_R2 <- loo_R2(.)
          x
          }) %>%
  bind_rows(.id="model") %>% 
  arrange(desc(loo_R2))

sjPlot::tab_model(h1_simple, bpe = "mean",show.ngroups = T,ci.hyphen = ";",
                  pred.labels = variable_labels)
equiv_test <- equivalence_test(h1_simple, range = c(-0.1, 0.1))
equiv_test_table <- equiv_test %>% 
  mutate(Parameter = recode(Parameter, !!!effect_labels)) %>% 
  mutate(
    ROPE_Percentage = sprintf("%2.f%%", 100*ROPE_Percentage),
    HDI = sprintf("[% .2f;% .2f]", HDI_low, HDI_high)) %>% 
  select(Parameter, H0 = ROPE_Equivalence, `inside ROPE` = ROPE_Percentage, `89% HDI` = HDI)
kable(equiv_test_table, caption = "Test whether the 89% highest-density interval (HDI) is fully within the region of practical equivalence (ROPE) of [-0.1;0.1] that we set (where all continuous variables, except age are standardised).")
plot(equiv_test) + scale_y_discrete("Effect", breaks = names(effect_labels), labels = effect_labels)
```

<details><summary>Model details</summary>

```{r}
summary(h1_simple)
summary(h1_after_diagnosis)
conditional_effects(h1_after_diagnosis_melsm)
# conditional_smooths(h1_after_diagnosis_melsm)
summary(h1_sex_mod_dataset_varying)
summary(h1_after_diagnosis_melsm)
kable(r2s, caption = "Explained variance, regular and leave-one-out.")
kable(coef(h1_sex_mod_dataset_varying)$dataset[, ,"f0"], caption = "Estimated association between f0 and outcome by dataset")
```

</details>


## Hypothesis 4: SOI behavior
Participants with lower voice pitch will report having a more unrestricted sociosexual behavior.

__Interpretation:__ The data are are consistent with substantial linear negative relationship
between `f0` and unrestricted sociosexuality. The 89% HDI for `f0`
falls entirely outside the ROPE, but the HDI for `pf` falls almost entirely within it. This
evidence is consistent with a non-negligible association, where people with deeper voices have
a less restricted sociosexuality (after adjusting for age and gender). Further research is needed to verify if the association with `pf` is truly negligible in size.


### Visually diagnose non-linearity
```{r,warning=FALSE}
ggplot(vcs, aes(f0, behavior)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(pf, behavior)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(age*10, behavior)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  scale_x_continuous("Age") +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 
```

__Decisions upon visual diagnosis:__ We will fit splines for f0, pf, and age. It seems
likely that the nonlinearities in f0 and pf will not both be apparent after adjusting for one
another. There is no evidence in the plots that there is an interaction with sex, except for age.

### Models
```{r}
h1_simple <- brm(behavior ~ f0 + pf + sex + age + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/behavior/h1_simple") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 


h1_after_diagnosis <- brm(behavior ~  s(f0) + s(pf) + sex + s(age, by = sex) + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, cores = chains, chains = chains,
          prior = priors, 
          control = control, save_mevars = TRUE,
          file = "models/behavior/h1_nonlinear") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 
conditional_smooths(h1_after_diagnosis)

compare_models <- loo_compare(h1_simple, h1_after_diagnosis)
compare_models

h1_sex_mod_dataset_varying <- brm(behavior ~ f0 + sex + s(age, by = sex) + 
                                    (1 + f0 + sex || dataset), data = vcs,
          prior = priors,
          iter = iter + 2000, warmup = warmup + 1000, cores = chains, chains = chains,
          control = control, save_mevars = TRUE,
          file = "models/behavior/h1_sex_mod_dataset_varying2") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

h1_after_diagnosis_melsm <- brm(
  bf(behavior ~  f0 + sex + s(age, by = sex) + (1 | dataset),
     sigma ~ f0 + sex + s(age, by = sex) + (1 | dataset)), data = vcs,
          prior = priors,
          iter = iter + 2000, warmup = warmup + 1000, cores = chains, chains = chains,
          control = control, save_mevars = TRUE,
          file = "models/behavior/h1_after_diagnosis_melsm") %>%
  add_criterion("loo") %>%
  add_criterion("bayes_R2") %>%
  add_criterion("loo_R2")

compare_models <- loo_compare(h1_simple, h1_after_diagnosis, h1_sex_mod_dataset_varying, h1_after_diagnosis_melsm)
compare_models

r2s <- list(h1_simple=h1_simple, h1_after_diagnosis=h1_after_diagnosis, h1_sex_mod_dataset_varying=h1_sex_mod_dataset_varying, h1_after_diagnosis_melsm=h1_after_diagnosis_melsm) %>% 
  map(~ { x <- as_tibble(bayes_R2(.))
          x$loo_R2 <- loo_R2(.)
          x
          }) %>%
  bind_rows(.id="model") %>% 
  arrange(desc(loo_R2))

sjPlot::tab_model(h1_simple, bpe = "mean",show.ngroups = T,ci.hyphen = ";",
                  pred.labels = variable_labels)

equiv_test <- equivalence_test(h1_simple, range = c(-0.1, 0.1))
equiv_test_table <- equiv_test %>% 
  mutate(Parameter = recode(Parameter, !!!effect_labels)) %>% 
  mutate(
    ROPE_Percentage = sprintf("%2.f%%", 100*ROPE_Percentage),
    HDI = sprintf("[% .2f;% .2f]", HDI_low, HDI_high)) %>% 
  select(Parameter, H0 = ROPE_Equivalence, `inside ROPE` = ROPE_Percentage, `89% HDI` = HDI)
kable(equiv_test_table, caption = "Test whether the 89% highest-density interval (HDI) is fully within the region of practical equivalence (ROPE) of [-0.1;0.1] that we set (where all continuous variables, except age are standardised).")
plot(equiv_test) + scale_y_discrete("Effect", breaks = names(effect_labels), labels = effect_labels)
```

<details><summary>Model details</summary>

```{r}
summary(h1_simple)
summary(h1_after_diagnosis)
conditional_effects(h1_simple)
conditional_smooths(h1_after_diagnosis)
summary(h1_sex_mod_dataset_varying)
summary(h1_after_diagnosis_melsm)
kable(r2s, caption = "Explained variance, regular and leave-one-out.")
kable(coef(h1_sex_mod_dataset_varying)$dataset[, ,"f0"], caption = "Estimated association between f0 and outcome by dataset")
equivalence_test(h1_after_diagnosis_melsm, range = c(-0.1, 0.1))
```

</details>



## Summary of results

### Models
```{r preregresults,fig.width=8, fig.height=10}
dominance <- readRDS("models/dominance/h1_simple.rds")
agree <- readRDS("models/agree/h1_simple2.rds")
extra <- readRDS("models/extra/h1_simple.rds")
soi <- readRDS("models/behavior/h1_simple.rds")
theme_set(theme_cowplot())

modify <- function(outcome) {
  list(scale_y_discrete(outcome, breaks = names(effect_labels), labels = effect_labels),
  guides(fill = "none"),
  theme(panel.spacing = unit(c(0), "cm"),
        plot.margin = unit(c(0, 0.5, 0, 0.5), "cm"))
)
}
remove_x_axis <- list(
  scale_x_continuous("", limits = c(-0.5, 0.4)),
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        axis.line.x = element_blank())
)

p_dominance <- plot(equivalence_test(dominance, parameters = c("b_f0", "b_pf", "b_sex1"))) + modify("Dominance") + remove_x_axis
p_agree <- plot(equivalence_test(agree, parameters = c("b_f0", "b_pf", "b_sex1"))) +
  modify("Agreeableness") + remove_x_axis
p_extra <- plot(equivalence_test(extra, parameters = c("b_f0", "b_pf", "b_sex1")))  +
  modify("Extraversion") + remove_x_axis
p_soi <- plot(equivalence_test(soi, parameters = c("b_f0", "b_pf", "b_sex1"))) +
  modify("SOI behavior") + xlim(c(-0.5, 0.4))
legend <- get_legend(
  p_dominance + 
    guides(fill = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom", legend.justification = "center")
)

neg_spacer <- -0.17
aligned_plots <- align_plots(p_dominance, p_extra, p_agree, p_soi, align="hv")
plot_grid(ncol = 1,  rel_heights = c(1, neg_spacer, 0.8, neg_spacer, 1, neg_spacer, 1.1, .15),
          aligned_plots[[1]], NULL, aligned_plots[[2]], NULL, aligned_plots[[3]],NULL, aligned_plots[[4]], legend)

ggsave("preregistered_rope.pdf", width = 8, height = 10)
```

### Tabular
```{r}
get_coefs <- function(model) {
model_summary <- summary(model)
nonvarying <- model_summary$fixed %>% 
  as.data.frame() %>% 
  rownames_to_column("term") %>% 
  mutate(group = "non-varying",
         outcome = as.character(model_summary$formula[[1]][[2]]))
varying <- model_summary$random %>% 
  map(~ rownames_to_column(as.data.frame(.), "term")) %>% 
  bind_rows(.id = "group") %>% 
  left_join(model_summary$ngrps %>% 
    as_tibble() %>% 
    gather(group, n), by = "group") %>% 
  mutate(#group = paste0(group, " (n=", n, ")"),
         outcome = as.character(model_summary$formula[[1]][[2]]))

two_digits <- function(x) { sprintf("%.2f", x) }
coefs <- bind_rows(nonvarying, 
                   varying)
coefs <- coefs %>% select(group, outcome, term, Estimate, `l-95% CI`, `u-95% CI`)
coefs$Estimate = two_digits(coefs$Estimate)
coefs$`l-95% CI` = two_digits(coefs$`l-95% CI`)
coefs$`u-95% CI` = two_digits(coefs$`u-95% CI`)
coefs
}

coefs <- bind_rows(get_coefs(dominance), 
                   get_coefs(extra), get_coefs(agree), get_coefs(soi))

wide_coefs <- coefs %>% 
  mutate(Estimate = paste0(Estimate, " [", `l-95% CI`, ";", `u-95% CI`, "]")) %>% 
    select(group, outcome, term, Estimate) %>% 
  mutate(term = recode(term, "meageage_se" = "Age(±SE)", "age" = "Age(±SE)"),
         outcome = fct_inorder(outcome),
         term = fct_inorder(term)) %>% 
  spread(outcome, Estimate) %>% 
  arrange(desc(group), term) %>% 
  mutate(group = fct_inorder(group))

outcome_names <- c("Extraversion" = "extra", "Dominance" = "dominance",
                   "Agreeableness" = "agree", "SOI behavior" = "behavior")

library(kableExtra)
wide_coefs %>% 
  mutate(term = str_replace_all(term, variable_labels)) %>% 
  rename(!!!syms(outcome_names), Term = term) %>% 
  select(-group) %>% 
  kable(caption = "Exploratory analysis results") %>%
  pack_rows(index = table(wide_coefs$group)) %>% 
  column_spec(column = 1, width = "3.3cm") %>% 
  column_spec(column = 2:(ncol(wide_coefs)-1), width = "3cm") %>% 
  add_header_above(c(" " = 1, "Estimated effect on each outcome [95% CI]" = ncol(wide_coefs)-2)) %>% 
  footnote("Estimated associations between outcomes, for which we had made preregistered predictions.")
```


### Scatterplots

```{r}
dominance <- ggplot(vcs, aes(f0, dominance)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(aes(colour = sex, fill = sex), method = "lm") +
  scale_color_manual("Sex", values = c("#40A5BF", "black")) +
  scale_fill_manual("Sex", values = c("#40A5BF", "black"))  +
  guides(color = F, fill = F) +
  xlab("") +
  ylab("Dominance") +
  theme(panel.spacing = unit(c(0), "cm"),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))

extra <- ggplot(vcs, aes(f0, extra)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(aes(colour = sex, fill = sex), method = "lm") +
  scale_color_manual("Sex", values = c("#40A5BF", "black")) +
  scale_fill_manual("Sex", values = c("#40A5BF", "black"))  +
  guides(color = F, fill = F) +
  xlab("") +
  ylab("Extraversion") +
  theme(panel.spacing = unit(c(0), "cm"),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))

agree <- ggplot(vcs, aes(f0, agree)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(aes(colour = sex, fill = sex), method = "lm") +
  scale_color_manual("Sex", values = c("#40A5BF", "black")) +
  scale_fill_manual("Sex", values = c("#40A5BF", "black"))  +
  guides(color = F, fill = F) +
  xlab("Voice pitch (f0)") +
  ylab("Agreeableness") +
  theme(panel.spacing = unit(c(0), "cm"),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))


behavior <- ggplot(vcs, aes(f0, behavior)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(aes(colour = sex, fill = sex), method = "lm") +
  scale_color_manual("Sex", values = c("#40A5BF", "black")) +
  scale_fill_manual("Sex", values = c("#40A5BF", "black"))  +
  guides(color = F, fill = F) +
  xlab("Voice pitch (f0)") +
  ylab("SOI Behavior") +
  theme(panel.spacing = unit(c(0), "cm"),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))


plot_grid(ncol = 2,  dominance, extra, agree, behavior, rel_heights = c(1, 1, 1, 1),
          align = "hv")
ggsave("scatterplots_prereg.pdf", width = 8, height = 8)
```

