---
title: "Preregistered analysis"
author: "Ruben Arslan"
date: "3/5/2019"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: "hide"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(brms)
library(sjPlot)
library(bayestestR)
library(labelled)
theme_set(theme_bw())
```

## Load data

```{r}
vcs <- rio::import("data_complete_all_anonym_allZ_unfiltered.xlsx")
var_label(vcs$dominance) <- "Dominance"
var_label(vcs$neuro) <- "Neuroticism"
var_label(vcs$agree) <- "Agreeableness"
var_label(vcs$extra) <- "Extraversion"
var_label(vcs$openn) <- "Openness"
var_label(vcs$consc) <- "Conscientiousness"
var_label(vcs$soi_full) <- "Unrestricted sociosexuality"
var_label(vcs$f0) <- "Voice pitch"
var_label(vcs$pf) <- "Formants"
vcs$sex_c <- vcs$sex
vcs$sex <- factor(if_else(vcs$sex == 1, "male", "female"))
contrasts(vcs$sex) <- contr.helmert(2)
var_label(vcs$sex) <- "Sex"
set.seed(1)
var_label(vcs$age) <- "Age"
vcs <- vcs %>% 
  mutate(
    age = if_else(dataset == 9, 20, age)/10,
    age_se = if_else(dataset == 9, 3, 0.5)/10
  )
warmup <- 2000
iter <- warmup + 2000
chains <- 4
control <- list(adapt_delta = 0.99)
priors <- c(
  prior(normal(0, 3), class = b)
)

variable_labels <- c("Intercept"= "Intercept",  "sex1" = "Sex [male]", "bsp_meageage_se" = "Age±SE", "f0" = "Voice pitch (f0)", "pf" = "Formants (f1-f4)", "age" = "Age")
effect_labels <- c("b_Intercept"= "Intercept",  "b_sex1" = "Sex [male]", "bsp_meageage_se" = "Age±SE", "b_f0" = "Voice pitch (f0)", "b_pf" = "Formants (f1-f4)", "b_age" = "Age")

```

## Missingness patterns
```{r}
codebook::md_pattern(vcs %>% select(dominance, neuro, agree, soi_full, sex, age, f0, pf, dataset))
vcs <- vcs %>% filter(!is.na(f0), !is.na(pf), !is.na(age))
```


## Hypothesis 1: Dominance

Participants with lower voice pitch will have a more dominant personality.

__Interpretation:__ The data are are consistent with substantial linear negative relationships
between `f0` and dominance. The 89% HDI for `f0` falls entirely outside the ROPE, but the HDI for `pf` falls almost entirely within it. This evidence is consistent with a non-negligible association, where people with deeper voices are more dominant (after adjusting for age and gender). Further research is needed to verify if the association with `pf` is truly negligible in size.

### Visually diagnose non-linearity
```{r,warning=FALSE}
ggplot(vcs, aes(f0, dominance)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(pf, dominance)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(age*10, dominance)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  scale_x_continuous("Age") +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 
```

__Decisions upon visual diagnosis:__ Visual diagnostic show no clear sign of nonlinearities. 
We will fit linear effects for f0, pf, and age. It is not necessary to model measurement error
in age, as dataset 9 (where age was not noted individually) is not included in these analyses.
Visually, there could be an interaction between sex and f0. 


### Models
```{r}
h1_simple <- brm(dominance ~ f0 + pf + sex + age + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/dominance/h1_simple") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 


h1_after_diagnosis <- brm(dominance ~ f0*sex + pf + sex + age + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, cores = chains, chains = chains,
          prior = priors, 
          control = control, save_mevars = TRUE,
          file = "models/dominance/h1_nonlinear") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 
# conditional_smooths(h1_after_diagnosis)

compare_models <- loo_compare(h1_simple, h1_after_diagnosis)
compare_models

h1_sex_mod_dataset_varying <- brm(dominance ~ f0 + sex + age + 
                                    (1 + f0 || dataset), data = vcs,
          prior = priors,
          iter = iter + 2000, warmup = warmup + 1000, cores = chains, chains = chains,
          control = control, save_mevars = TRUE,
          file = "models/dominance/h1_sex_mod_dataset_varying") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

h1_after_diagnosis_melsm <- brm(
  bf(dominance ~ f0 + sex + age + (1 | dataset),
     sigma ~ f0 + sex + age + (1 | dataset)), data = vcs,
          prior = priors,
          iter = iter + 2000, warmup = warmup + 1000, cores = chains, chains = chains,
          control = control, save_mevars = TRUE,
          file = "models/dominance/h1_after_diagnosis_melsm") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 
  

compare_models <- loo_compare(h1_simple, h1_after_diagnosis, h1_sex_mod_dataset_varying,
                      h1_after_diagnosis_melsm)
compare_models

r2s <- list(h1_simple=h1_simple, h1_after_diagnosis=h1_after_diagnosis, h1_sex_mod_dataset_varying=h1_sex_mod_dataset_varying,
                      h1_after_diagnosis_melsm=h1_after_diagnosis_melsm) %>% 
  map(~ { x <- as_tibble(bayes_R2(.))
          x$loo_R2 <- loo_R2(.)
          x
          }) %>%
  bind_rows(.id="model") %>% 
  arrange(desc(loo_R2))

sjPlot::tab_model(h1_simple, bpe = "mean",show.ngroups = T,ci.hyphen = ";",
                  pred.labels = variable_labels)
equiv_test <- equivalence_test(h1_simple, range = c(-0.1, 0.1))
equiv_test_table <- equiv_test %>% 
  mutate(Parameter = recode(Parameter, !!!effect_labels)) %>% 
  mutate(
    ROPE_Percentage = sprintf("%2.f%%", 100*ROPE_Percentage),
    HDI = sprintf("[% .2f;% .2f]", HDI_low, HDI_high)) %>% 
  select(Parameter, H0 = ROPE_Equivalence, `inside ROPE` = ROPE_Percentage, `89% HDI` = HDI)
kable(equiv_test_table, caption = "Test whether the 89% highest-density interval (HDI) is fully within the region of practical equivalence (ROPE) of [-0.1;0.1] that we set (where all continuous variables, except age are standardised).")
plot(equiv_test) + scale_y_discrete("Effect", breaks = names(effect_labels), labels = effect_labels)
```

<details><summary>Model details</summary>

```{r}
summary(h1_simple)
summary(h1_after_diagnosis)
conditional_effects(h1_after_diagnosis_melsm)
# conditional_smooths(h1_after_diagnosis)
summary(h1_sex_mod_dataset_varying)
summary(h1_after_diagnosis_melsm)
kable(r2s, caption = "Explained variance, regular and leave-one-out.")
kable(coef(h1_sex_mod_dataset_varying)$dataset[, ,"f0"], caption = "Estimated association between f0 and outcome by dataset")
```

</details>


## Hypothesis 2: Agreeableness

Participants with lower voice pitch will score higher on agreeableness.

__Interpretation:__ The credible intervals for `f0` and `pf` include zero, but the 89% HDI does not fall entirely within the ROPE.  This evidence is consistent with a negligible association between `f0`/`pf` and agreeableness. Further research is needed to verify if the associations are truly negligible in size.


### Visually diagnose non-linearity
```{r,warning=FALSE}
ggplot(vcs, aes(f0, agree)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour =  "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(pf, agree)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(age*10, agree)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  scale_x_continuous("Age") +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 
```

__Decisions upon visual diagnosis:__ Visual diagnostic shows signs of nonlinearity for f0 and pf, but no clear interactions by sex.
We will fit splines for f0, and pf. It is necessary to model measurement error
in age, as dataset 9 (where age was not noted individually) is included in these analyses.


### Models
```{r}
h1_simple <- brm(agree ~ f0 + pf + sex + me(age, age_se) + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/agree/h1_simple") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 


h1_after_diagnosis <- brm(agree ~ s(f0) + s(pf) + sex + me(age, age_se) + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, cores = chains, chains = chains,
          prior = priors, 
          control = control, save_mevars = TRUE,
          file = "models/agree/h1_nonlinear") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 
conditional_smooths(h1_after_diagnosis)

compare_models <- loo_compare(h1_simple, h1_after_diagnosis)
compare_models

h1_sex_mod_dataset_varying <- brm(agree ~ f0 + pf + f0 * sex + me(age, age_se) + 
                                    (1 + f0 + pf + sex || dataset), data = vcs,
          prior = priors,
          iter = iter + 2000, warmup = warmup + 1000, cores = chains, chains = chains,
          control = control, save_mevars = TRUE,
          file = "models/agree/h1_sex_mod_dataset_varying") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

h1_after_diagnosis_melsm <- brm(
  bf(agree ~ s(f0) + s(pf) + sex + me(age, age_se) + (1 | dataset),
     sigma ~ s(f0) + s(pf) + sex + me(age, age_se) + (1 | dataset)), data = vcs,
          prior = priors,
          iter = iter + 2000, warmup = warmup + 1000, cores = chains, chains = chains,
          control = control, save_mevars = TRUE,
          file = "models/agree/h1_after_diagnosis_melsm") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 
  

compare_models <- loo_compare(h1_simple, h1_after_diagnosis, h1_sex_mod_dataset_varying,
                      h1_after_diagnosis_melsm)
compare_models
r2s <- list(h1_simple=h1_simple, h1_after_diagnosis=h1_after_diagnosis, h1_sex_mod_dataset_varying=h1_sex_mod_dataset_varying,
                      h1_after_diagnosis_melsm=h1_after_diagnosis_melsm) %>% 
  map(~ { x <- as_tibble(bayes_R2(.))
          x$loo_R2 <- loo_R2(.)
          x
          }) %>%
  bind_rows(.id="model") %>% 
  arrange(desc(loo_R2))

sjPlot::tab_model(h1_simple, bpe = "mean",show.ngroups = T,ci.hyphen = ";",
                  pred.labels = variable_labels)
equiv_test <- equivalence_test(h1_simple, range = c(-0.1, 0.1))
equiv_test_table <- equiv_test %>% 
  mutate(Parameter = recode(Parameter, !!!effect_labels)) %>% 
  mutate(
    ROPE_Percentage = sprintf("%2.f%%", 100*ROPE_Percentage),
    HDI = sprintf("[% .2f;% .2f]", HDI_low, HDI_high)) %>% 
  select(Parameter, H0 = ROPE_Equivalence, `inside ROPE` = ROPE_Percentage, `89% HDI` = HDI)
kable(equiv_test_table, caption = "Test whether the 89% highest-density interval (HDI) is fully within the region of practical equivalence (ROPE) of [-0.1;0.1] that we set (where all continuous variables, except age are standardised).")
plot(equiv_test) + scale_y_discrete("Effect", breaks = names(effect_labels), labels = effect_labels)
```

<details><summary>Model details</summary>

```{r}
summary(h1_simple)
summary(h1_after_diagnosis)
conditional_effects(h1_after_diagnosis_melsm)
# conditional_smooths(h1_after_diagnosis_melsm)
summary(h1_sex_mod_dataset_varying)
summary(h1_after_diagnosis_melsm)
kable(r2s, caption = "Explained variance, regular and leave-one-out.")
kable(coef(h1_sex_mod_dataset_varying)$dataset[, ,"f0"], caption = "Estimated association between f0 and outcome by dataset")
```

</details>

## Hypothesis 3:  Neuroticism

Participants with lower voice pitch will score lower on neuroticism.

__Interpretation:__ The data are are consistent with linear positive relationship
between `f0` and neuroticism. The 89% HDI for `f0`
excludes zero but partly inside the ROPE. 69% of the HDI for `pf` falls within the ROPE. This
evidence is consistent with an association, where people with deeper voices have
lower neuroticism (after adjusting for age and gender), but further research is needed to test whether the associations with `f0` and `pf` are negligible in size.


### Visually diagnose non-linearity
```{r,warning=FALSE}
ggplot(vcs, aes(f0, neuro)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour =  "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(pf, neuro)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(age*10, neuro)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  scale_x_continuous("Age") +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 
```

__Decisions upon visual diagnosis:__ Visual diagnostic shows signs of a potential interaction by sex f0 and a potential interaction by sex coupled with nonlinearity for pf.
We will fit an interaction for f0, and separate splines by sex for pf. It is necessary to model measurement error in age, as dataset 9 (where age was not noted individually) is included in these analyses.


### Models
```{r}
h1_simple <- brm(neuro ~ f0 + pf + sex + me(age, age_se) + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/neuro/h1_simple") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 


h1_after_diagnosis <- brm(neuro ~ f0 * sex + s(pf, by = sex) + sex + me(age, age_se) + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, cores = chains, chains = chains,
          prior = priors, 
          control = control, save_mevars = TRUE,
          file = "models/neuro/h1_nonlinear") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 
conditional_smooths(h1_after_diagnosis)

compare_models <- loo_compare(h1_simple, h1_after_diagnosis)
compare_models

h1_sex_mod_dataset_varying <- brm(neuro ~ f0 + sex + me(age, age_se) + 
                                    (1 + f0 + sex + age || dataset), data = vcs,
          prior = priors,
          iter = iter + 2000, warmup = warmup + 1000, cores = chains, chains = chains,
          control = control, save_mevars = TRUE,
          file = "models/neuro/h1_sex_mod_dataset_varying") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

h1_after_diagnosis_melsm <- brm(
  bf(neuro ~ f0 + sex + me(age, age_se) + (1 | dataset),
     sigma ~ f0 + sex + me(age, age_se) + (1 | dataset)), data = vcs,
          prior = priors,
          iter = iter + 2000, warmup = warmup + 1000, cores = chains, chains = chains,
          control = control, save_mevars = TRUE,
          file = "models/neuro/h1_after_diagnosis_melsm") %>%
  add_criterion("loo") %>%
  add_criterion("bayes_R2") %>%
  add_criterion("loo_R2")


compare_models <- loo_compare(h1_simple, h1_after_diagnosis, h1_sex_mod_dataset_varying ,h1_after_diagnosis_melsm
                      )
compare_models
r2s <- list(h1_simple=h1_simple, h1_after_diagnosis=h1_after_diagnosis, h1_sex_mod_dataset_varying=h1_sex_mod_dataset_varying,h1_after_diagnosis_melsm=h1_after_diagnosis_melsm) %>% 
  map(~ { x <- as_tibble(bayes_R2(.))
          x$loo_R2 <- loo_R2(.)
          x
          }) %>%
  bind_rows(.id="model") %>% 
  arrange(desc(loo_R2))

sjPlot::tab_model(h1_simple, bpe = "mean",show.ngroups = T,ci.hyphen = ";",
                  pred.labels = variable_labels)
equiv_test <- equivalence_test(h1_simple, range = c(-0.1, 0.1))
equiv_test_table <- equiv_test %>% 
  mutate(Parameter = recode(Parameter, !!!effect_labels)) %>% 
  mutate(
    ROPE_Percentage = sprintf("%2.f%%", 100*ROPE_Percentage),
    HDI = sprintf("[% .2f;% .2f]", HDI_low, HDI_high)) %>% 
  select(Parameter, H0 = ROPE_Equivalence, `inside ROPE` = ROPE_Percentage, `89% HDI` = HDI)
kable(equiv_test_table, caption = "Test whether the 89% highest-density interval (HDI) is fully within the region of practical equivalence (ROPE) of [-0.1;0.1] that we set (where all continuous variables, except age are standardised).")
plot(equiv_test) + scale_y_discrete("Effect", breaks = names(effect_labels), labels = effect_labels)
```

<details><summary>Model details</summary>

```{r}
summary(h1_simple)
summary(h1_after_diagnosis)
conditional_effects(h1_after_diagnosis_melsm)
# conditional_smooths(h1_after_diagnosis_melsm)
summary(h1_sex_mod_dataset_varying)
# summary(h1_after_diagnosis_melsm)
kable(r2s, caption = "Explained variance, regular and leave-one-out.")
kable(coef(h1_sex_mod_dataset_varying)$dataset[, ,"f0"], caption = "Estimated association between f0 and outcome by dataset")
```

</details>

## Hypothesis 4: Sociosexuality
Participants with lower voice pitch will report having a more unrestricted sociosexuality.

__Interpretation:__ The data are are consistent with substantial linear negative relationship
between `f0` and unrestricted sociosexuality. The 89% HDI for `f0`
falls entirely outside the ROPE, but the HDI for `pf` falls almost entirely within it. This
evidence is consistent with a non-negligible association, where people with deeper voices have
a less restricted sociosexuality (after adjusting for age and gender). Further research is needed to verify if the association with `pf` is truly negligible in size.


### Visually diagnose non-linearity
```{r,warning=FALSE}
ggplot(vcs, aes(f0, soi_full)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(pf, soi_full)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(age*10, soi_full)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  scale_x_continuous("Age") +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 
```

__Decisions upon visual diagnosis:__ We will fit splines for f0, pf, and age. It seems
likely that the nonlinearities in f0 and pf will not both be apparent after adjusting for one
another. There is no evidence in the plots that there is an interaction with sex, except for age.

### Models
```{r}
h1_simple <- brm(soi_full ~ f0 + pf + sex + age + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/soi_full/h1_simple") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 


h1_after_diagnosis <- brm(soi_full ~  s(f0) + s(pf) + sex + s(age, by = sex) + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, cores = chains, chains = chains,
          prior = priors, 
          control = control, save_mevars = TRUE,
          file = "models/soi_full/h1_nonlinear") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 
conditional_smooths(h1_after_diagnosis)

compare_models <- loo_compare(h1_simple, h1_after_diagnosis)
compare_models

h1_sex_mod_dataset_varying <- brm(soi_full ~ f0 + sex + s(age, by = sex) + 
                                    (1 + f0 + sex + age || dataset), data = vcs,
          prior = priors,
          iter = iter + 2000, warmup = warmup + 1000, cores = chains, chains = chains,
          control = control, save_mevars = TRUE,
          file = "models/soi_full/h1_sex_mod_dataset_varying") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

h1_after_diagnosis_melsm <- brm(
  bf(soi_full ~  f0 + sex + s(age, by = sex) + (1 | dataset),
     sigma ~ f0 + sex + s(age, by = sex) + (1 | dataset)), data = vcs,
          prior = priors,
          iter = iter + 2000, warmup = warmup + 1000, cores = chains, chains = chains,
          control = control, save_mevars = TRUE,
          file = "models/soi_full/h1_after_diagnosis_melsm") %>%
  add_criterion("loo") %>%
  add_criterion("bayes_R2") %>%
  add_criterion("loo_R2")

compare_models <- loo_compare(h1_simple, h1_after_diagnosis, h1_sex_mod_dataset_varying, h1_after_diagnosis_melsm)
compare_models
r2s <- list(h1_simple=h1_simple, h1_after_diagnosis=h1_after_diagnosis, h1_sex_mod_dataset_varying=h1_sex_mod_dataset_varying, h1_after_diagnosis_melsm=h1_after_diagnosis_melsm) %>% 
  map(~ { x <- as_tibble(bayes_R2(.))
          x$loo_R2 <- loo_R2(.)
          x
          }) %>%
  bind_rows(.id="model") %>% 
  arrange(desc(loo_R2))

sjPlot::tab_model(h1_simple, bpe = "mean",show.ngroups = T,ci.hyphen = ";",
                  pred.labels = variable_labels)
equiv_test <- equivalence_test(h1_simple, range = c(-0.1, 0.1))
equiv_test_table <- equiv_test %>% 
  mutate(Parameter = recode(Parameter, !!!effect_labels)) %>% 
  mutate(
    ROPE_Percentage = sprintf("%2.f%%", 100*ROPE_Percentage),
    HDI = sprintf("[% .2f;% .2f]", HDI_low, HDI_high)) %>% 
  select(Parameter, H0 = ROPE_Equivalence, `inside ROPE` = ROPE_Percentage, `89% HDI` = HDI)
kable(equiv_test_table, caption = "Test whether the 89% highest-density interval (HDI) is fully within the region of practical equivalence (ROPE) of [-0.1;0.1] that we set (where all continuous variables, except age are standardised).")
plot(equiv_test) + scale_y_discrete("Effect", breaks = names(effect_labels), labels = effect_labels)
```

<details><summary>Model details</summary>

```{r}
summary(h1_simple)
summary(h1_after_diagnosis)
conditional_effects(h1_simple)
conditional_smooths(h1_after_diagnosis)
summary(h1_sex_mod_dataset_varying)
summary(h1_after_diagnosis_melsm)
kable(r2s, caption = "Explained variance, regular and leave-one-out.")
kable(coef(h1_sex_mod_dataset_varying)$dataset[, ,"f0"], caption = "Estimated association between f0 and outcome by dataset")
```

</details>

