---
title: "Preregistered analysis"
author: "Ruben Arslan"
date: "3/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(brms)
library(sjPlot)
library(bayestestR)
library(labelled)
theme_set(theme_bw())
```

## Load data

```{r}
vcs <- rio::import("data_complete_all_anonym_allZ.xlsx")
var_label(vcs$dominance) <- "Dominance"
var_label(vcs$neuro) <- "Neuroticism"
var_label(vcs$agree) <- "Agreeableness"
var_label(vcs$extra) <- "Extraversion"
var_label(vcs$openn) <- "Openness"
var_label(vcs$consc) <- "Conscientiousness"
var_label(vcs$soi_full) <- "Unrestricted sociosexuality"
var_label(vcs$f0) <- "Voice pitch"
var_label(vcs$pf) <- "Formants"
vcs$sex_c <- vcs$sex
vcs$sex <- factor(if_else(vcs$sex == 1, "male", "female"))
contrasts(vcs$sex) <- contr.helmert(2)
var_label(vcs$sex) <- "Sex"
set.seed(1)
var_label(vcs$age) <- "Age"
vcs <- vcs %>% 
  mutate(
    age = if_else(dataset == 9, 20, age)/10,
    age_se = if_else(dataset == 9, 3, 0.5)/10
  )
warmup <- 2000
iter <- warmup + 2000
chains <- 4
control <- list(adapt_delta = 0.99)
priors <- c(
  prior(normal(0, 3), class = b)
)

variable_labels <- c("Intercept"= "Intercept",  "sex1" = "Sex [male]", "bsp_meageage_se" = "Age±SE", "f0" = "Voice pitch (f0)", "pf" = "Formants (f1-f4)")

```

## Missingness patterns
```{r}
codebook::md_pattern(vcs %>% select(dominance, sex, age, f0, pf, dataset))
vcs <- vcs %>% filter(!is.na(f0), !is.na(pf), !is.na(age))
```


## Hypothesis 1: 

Participants with lower voice pitch will have a more dominant personality.

__Interpretation:__ The data are inconclusive

### Visually diagnose non-linearity
```{r}
ggplot(vcs, aes(f0, dominance)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(pf, dominance)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(age*10, dominance)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  scale_x_continuous("Age") +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 
```

__Decisions upon visual diagnosis:__ Visual diagnostic show no clear sign of nonlinearities. 
We will fit linear effects for f0, pf, and age. It is not necessary to model measurement error
in age, as dataset 9 (where age was not noted individually) is not included in these analyses.
Visually, there could be an interaction between sex and f0. 


### Models
```{r}
h1_simple <- brm(dominance ~ f0 + pf + sex + age + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/dominance/h1_simple") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 


h1_after_diagnosis <- brm(dominance ~ f0*sex + pf + sex + age + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, cores = chains, chains = chains,
          prior = priors, 
          control = control, save_mevars = TRUE,
          file = "models/dominance/h1_nonlinear") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 
conditional_smooths(h1_after_diagnosis)

h1_sex_mod_dataset_varying <- brm(dominance ~ f0 + pf + f0 * sex + age + 
                                    (1 + f0 * sex || dataset), data = vcs,
          prior = priors,
          iter = iter + 2000, warmup = warmup + 1000, cores = chains, chains = chains,
          control = control, save_mevars = TRUE,
          file = "models/dominance/h1_sex_mod_dataset_varying") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

h1_after_diagnosis_melsm <- brm(
  bf(dominance ~ f0*sex + pf + sex + age + (1 | dataset),
     sigma ~ f0*sex + pf + sex + age + (1 | dataset)), data = vcs,
          prior = priors,
          iter = iter + 2000, warmup = warmup + 1000, cores = chains, chains = chains,
          control = control, save_mevars = TRUE,
          file = "models/dominance/h1_after_diagnosis_melsm") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 
  

compare_models <- loo_compare(h1_simple, h1_after_diagnosis, h1_sex_mod_dataset_varying,
                      h1_after_diagnosis_melsm)
compare_models
r2s <- list(h1_simple=h1_simple, h1_after_diagnosis=h1_after_diagnosis, h1_sex_mod_dataset_varying=h1_sex_mod_dataset_varying,
                      h1_after_diagnosis_melsm=h1_after_diagnosis_melsm) %>% 
  map(~ { x <- as_tibble(bayes_R2(.))
          x$loo_R2 <- loo_R2(.)
          x
          }) %>%
  bind_rows(.id="model") %>% 
  arrange(desc(loo_R2))

sjPlot::tab_model(h1_simple, bpe = "mean",show.ngroups = T,ci.hyphen = ";",
                  terms = variable_labels)
equiv_test <- equivalence_test(h1_simple, range = c(-0.1, 0.1)) %>% 
  mutate(Parameter = recode(Parameter, !!!variable_labels))
kable(equiv_test, caption = "Test whether the 89% highest-density interval (HDI) is fully within the region of practical equivalence (ROPE) of [-0.1;0.1] that we set (where all continuous variables, except age are standardised).")
plot(equiv_test)
```

<details><summary>Model details</summary>

```{r}
summary(h1_simple)
summary(h1_after_diagnosis)
conditional_effects(h1_after_diagnosis_melsm)
conditional_smooths(h1_after_diagnosis_melsm)
summary(h1_sex_mod_dataset_varying)
summary(h1_after_diagnosis_melsm)
kable(r2s, caption = "Explained variance, regular and leave-one-out.")
```

</details>


## Hypothesis 2: 
Participants with lower voice pitch will score higher on agreeableness.


### Visually diagnose non-linearity
```{r}
ggplot(vcs, aes(f0, agree)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour =  "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(pf, agree)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(age*10, agree)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  scale_x_continuous("Age") +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 
```

__Decisions upon visual diagnosis:__ Visual diagnostic shows signs of nonlinearity for f0 and pf, but no clear interactions by sex.
We will fit splines for f0, and pf. It is necessary to model measurement error
in age, as dataset 9 (where age was not noted individually) is included in these analyses.


### Models
```{r}
h1_simple <- brm(agree ~ f0 + pf + sex + me(age, age_se) + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/agree/h1_simple") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 


h1_after_diagnosis <- brm(agree ~ s(f0) + s(pf) + sex + me(age, age_se) + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, cores = chains, chains = chains,
          prior = priors, 
          control = control, save_mevars = TRUE,
          file = "models/agree/h1_nonlinear") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 
conditional_smooths(h1_after_diagnosis)

h1_sex_mod_dataset_varying <- brm(agree ~ f0 + pf + f0 * sex + me(age, age_se) + 
                                    (1 + f0 + pf + sex || dataset), data = vcs,
          prior = priors,
          iter = iter + 2000, warmup = warmup + 1000, cores = chains, chains = chains,
          control = control, save_mevars = TRUE,
          file = "models/agree/h1_sex_mod_dataset_varying") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

h1_after_diagnosis_melsm <- brm(
  bf(agree ~ s(f0) + s(pf) + sex + me(age, age_se) + (1 | dataset),
     sigma ~ s(f0) + s(pf) + sex + me(age, age_se) + (1 | dataset)), data = vcs,
          prior = priors,
          iter = iter + 2000, warmup = warmup + 1000, cores = chains, chains = chains,
          control = control, save_mevars = TRUE,
          file = "models/agree/h1_after_diagnosis_melsm") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 
  

compare_models <- loo_compare(h1_simple, h1_after_diagnosis, h1_sex_mod_dataset_varying,
                      h1_after_diagnosis_melsm)
compare_models
r2s <- list(h1_simple=h1_simple, h1_after_diagnosis=h1_after_diagnosis, h1_sex_mod_dataset_varying=h1_sex_mod_dataset_varying,
                      h1_after_diagnosis_melsm=h1_after_diagnosis_melsm) %>% 
  map(~ { x <- as_tibble(bayes_R2(.))
          x$loo_R2 <- loo_R2(.)
          x
          }) %>%
  bind_rows(.id="model") %>% 
  arrange(desc(loo_R2))

sjPlot::tab_model(h1_simple, bpe = "mean",show.ngroups = T,ci.hyphen = ";",
                  terms = variable_labels)
equiv_test <- equivalence_test(h1_simple, range = c(-0.1, 0.1)) %>% 
  mutate(Parameter = recode(Parameter, !!!variable_labels))
kable(equiv_test, caption = "Test whether the 89% highest-density interval (HDI) is fully within the region of practical equivalence (ROPE) of [-0.1;0.1] that we set (where all continuous variables, except age are standardised).")
plot(equiv_test)
```

<details><summary>Model details</summary>

```{r}
summary(h1_simple)
summary(h1_after_diagnosis)
conditional_effects(h1_after_diagnosis_melsm)
conditional_smooths(h1_after_diagnosis_melsm)
summary(h1_sex_mod_dataset_varying)
summary(h1_after_diagnosis_melsm)
kable(r2s, caption = "Explained variance, regular and leave-one-out.")
```

</details>

## Hypothesis 3: 
Participants with lower voice pitch will score lower on neuroticism.


### Visually diagnose non-linearity
```{r}
ggplot(vcs, aes(f0, neuro)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour =  "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(pf, neuro)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(age*10, neuro)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  scale_x_continuous("Age") +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 
```

__Decisions upon visual diagnosis:__ Visual diagnostic shows signs of a potential interaction by sex f0 and a potential interaction by sex coupled with nonlinearity for pf.
We will fit an interaction for f0, and separate splines by sex for pf. It is necessary to model measurement error in age, as dataset 9 (where age was not noted individually) is included in these analyses.


### Models
```{r}
h1_simple <- brm(neuro ~ f0 + pf + sex + me(age, age_se) + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/neuro/h1_simple") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 


h1_after_diagnosis <- brm(neuro ~ f0 * sex + s(pf, by = sex) + sex + me(age, age_se) + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, cores = chains, chains = chains,
          prior = priors, 
          control = control, save_mevars = TRUE,
          file = "models/neuro/h1_nonlinear") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 
conditional_smooths(h1_after_diagnosis)

h1_sex_mod_dataset_varying <- brm(neuro ~ f0 + pf * sex + f0 * sex + me(age, age_se) + 
                                    (1 + f0*sex + pf*sex + sex || dataset), data = vcs,
          prior = priors,
          iter = iter + 2000, warmup = warmup + 1000, cores = chains, chains = chains,
          control = control, save_mevars = TRUE,
          file = "models/neuro/h1_sex_mod_dataset_varying") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

h1_after_diagnosis_melsm <- brm(
  bf(neuro ~ f0 * sex + s(pf, by = sex) + sex + me(age, age_se) + (1 | dataset),
     sigma ~ f0 * sex + s(pf, by = sex) + sex + me(age, age_se) + (1 | dataset)), data = vcs,
          prior = priors,
          iter = iter + 2000, warmup = warmup + 1000, cores = chains, chains = chains,
          control = control, save_mevars = TRUE,
          file = "models/neuro/h1_after_diagnosis_melsm") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 
  

compare_models <- loo_compare(h1_simple, h1_after_diagnosis, h1_sex_mod_dataset_varying,
                      h1_after_diagnosis_melsm)
compare_models
r2s <- list(h1_simple=h1_simple, h1_after_diagnosis=h1_after_diagnosis, h1_sex_mod_dataset_varying=h1_sex_mod_dataset_varying,
                      h1_after_diagnosis_melsm=h1_after_diagnosis_melsm) %>% 
  map(~ { x <- as_tibble(bayes_R2(.))
          x$loo_R2 <- loo_R2(.)
          x
          }) %>%
  bind_rows(.id="model") %>% 
  arrange(desc(loo_R2))

sjPlot::tab_model(h1_simple, bpe = "mean",show.ngroups = T,ci.hyphen = ";",
                  terms = variable_labels)
equiv_test <- equivalence_test(h1_simple, range = c(-0.1, 0.1)) %>% 
  mutate(Parameter = recode(Parameter, !!!variable_labels))
kable(equiv_test, caption = "Test whether the 89% highest-density interval (HDI) is fully within the region of practical equivalence (ROPE) of [-0.1;0.1] that we set (where all continuous variables, except age are standardised).")
plot(equiv_test)
```

<details><summary>Model details</summary>

```{r}
summary(h1_simple)
summary(h1_after_diagnosis)
conditional_effects(h1_after_diagnosis_melsm)
conditional_smooths(h1_after_diagnosis_melsm)
summary(h1_sex_mod_dataset_varying)
summary(h1_after_diagnosis_melsm)
kable(r2s, caption = "Explained variance, regular and leave-one-out.")
```

</details>

## Hypothesis 4: 
Participants with lower voice pitch will report having a more unrestricted sociosexuality.

__Interpretation:__ The data are are consistent with simple, linear, negative relationships
between `f0` and `pf` and unrestricted sociosexuality. While the 89% HDI for `f0`
falls entirely outside the ROPE, the HDI for `pf` falls almost entirely within the ROPE. This
evidence is consistent with a non-negligible association, where people with deeper voices have
a less restricted sociosexuality (after adjusting for age and gender). Further research is needed
to verify if the association with `pf` is replicable and non-negligible.


### Visually diagnose non-linearity
```{r}
ggplot(vcs, aes(f0, soi_full)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(pf, soi_full)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(age*10, soi_full)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  scale_x_continuous("Age") +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 
```

__Decisions upon visual diagnosis:__ We will fit splines for f0, pf, and age. It seems
likely that the nonlinearities in f0 and pf will not both be apparent after adjusting for one
another. There is no evidence in the plots that there is an interaction with sex, except for age.

### Models
```{r}
h1_simple <- brm(soi_full ~ f0 + pf + sex + age + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/soi_full/h1_simple") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 


h1_after_diagnosis <- brm(soi_full ~  s(f0) + s(pf) + sex + s(age, by = sex) + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, cores = chains, chains = chains,
          prior = priors, 
          control = control, save_mevars = TRUE,
          file = "models/soi_full/h1_nonlinear") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 
conditional_smooths(h1_after_diagnosis)

h1_sex_mod_dataset_varying <- brm(soi_full ~ f0 + pf * sex + s(age, by = sex) + 
                                    (1 + pf + f0 + sex || dataset), data = vcs,
          prior = priors,
          iter = iter + 2000, warmup = warmup + 1000, cores = chains, chains = chains,
          control = control, save_mevars = TRUE,
          file = "models/soi_full/h1_sex_mod_dataset_varying") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

h1_after_diagnosis_melsm <- brm(
  bf(soi_full ~ f0 + pf + sex + s(age, by = sex) + (1 | dataset),
     sigma ~ f0 + pf + sex + s(age, by = sex) + (1 | dataset)), data = vcs,
          prior = priors,
          iter = iter + 2000, warmup = warmup + 1000, cores = chains, chains = chains,
          control = control, save_mevars = TRUE,
          file = "models/soi_full/h1_after_diagnosis_melsm") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

compare_models <- loo_compare(h1_simple, h1_after_diagnosis, h1_sex_mod_dataset_varying,
                      h1_after_diagnosis_melsm)
compare_models
r2s <- list(h1_simple=h1_simple, h1_after_diagnosis=h1_after_diagnosis, h1_sex_mod_dataset_varying=h1_sex_mod_dataset_varying,
                      h1_after_diagnosis_melsm=h1_after_diagnosis_melsm) %>% 
  map(~ { x <- as_tibble(bayes_R2(.))
          x$loo_R2 <- loo_R2(.)
          x
          }) %>%
  bind_rows(.id="model") %>% 
  arrange(desc(loo_R2))

sjPlot::tab_model(h1_simple, bpe = "mean",show.ngroups = T,ci.hyphen = ";",
                  terms = variable_labels)
equiv_test <- equivalence_test(h1_simple, range = c(-0.1, 0.1)) %>% 
  mutate(Parameter = recode(Parameter, !!!variable_labels))
kable(equiv_test, caption = "Test whether the 89% highest-density interval (HDI) is fully within the region of practical equivalence (ROPE) of [-0.1;0.1] that we set (where all continuous variables, except age are standardised).")
plot(equiv_test)
```

<details><summary>Model details</summary>

```{r}
summary(h1_simple)
summary(h1_after_diagnosis)
conditional_effects(h1_after_diagnosis_melsm)
conditional_smooths(h1_after_diagnosis_melsm)
summary(h1_sex_mod_dataset_varying)
summary(h1_after_diagnosis_melsm)
kable(r2s, caption = "Explained variance, regular and leave-one-out.")
```

</details>

