---
title: "Preregistered analysis"
author: "Ruben Arslan"
date: "3/5/2019"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(brms)
library(sjPlot)
library(bayestestR)
library(labelled)
theme_set(theme_bw())
```

## Load data

```{r}
vcs <- rio::import("simulated_data_080319.xlsx")
var_label(vcs$dominance) <- "Dominance"
var_label(vcs$f0) <- "Voice pitch"
var_label(vcs$pf) <- "Formants"
vcs$sex_c <- vcs$sex
vcs$sex <- factor(if_else(vcs$sex == 1, "male", "female"))
contrasts(vcs$sex) <- contr.helmert(2)
var_label(vcs$sex) <- "Sex"
set.seed(1)
var_label(vcs$age) <- "Age"
vcs <- vcs %>% 
  mutate(
    age_se = if_else(dataset == 9, 3, 0.5)
  )
warmup <- 2000
iter <- warmup + 2000
chains <- 4
control <- list(adapt_delta = 0.99)
priors <- c(
  prior(normal(0, 3), class = b)
)
```

## Missingness patterns
```{r}
codebook::md_pattern(vcs %>% select(dominance, sex, age, f0, dataset))
```


## Hypothesis 1: 

### Simulate fake effect on dominance
```{r}
set.seed(1)
vcs <- vcs %>% mutate(
  f0 = 0.3 * rnorm(n()) + -0.3 * sex_c + rnorm(n()),
  dominance = 0.4 * sex_c + -0.4 * f0 + -0.1 * if_else(sex_c == 1, 1, 0) * (f0-1)^2 + 0.95 * rnorm(n())
)
var_label(vcs$dominance) <- "Dominance"
```

Participants with lower voice pitch will have a more dominant personality.

### Visually diagnose non-linearity
```{r}
ggplot(vcs, aes(f0, dominance)) + 
  geom_jitter(aes(colour = factor(sex)), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = factor(sex), fill = factor(sex)), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex", breaks = c(-1,1), labels = c("female", "male")) +
  scale_fill_viridis_d("Sex", breaks = c(-1,1), labels = c("female", "male")) 

ggplot(vcs, aes(pf, dominance)) + 
  geom_jitter(aes(colour = factor(sex)), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = factor(sex), fill = factor(sex)), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex", breaks = c(-1,1), labels = c("female", "male")) +
  scale_fill_viridis_d("Sex", breaks = c(-1,1), labels = c("female", "male")) 

ggplot(vcs, aes(age, dominance)) + 
  geom_jitter(aes(colour = factor(sex)), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = factor(sex), fill = factor(sex)), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex", breaks = c(-1,1), labels = c("female", "male")) +
  scale_fill_viridis_d("Sex", breaks = c(-1,1), labels = c("female", "male")) 
```


### Models
```{r}
h1_simple <- brm(dominance ~ f0 + pf + sex + me(age, age_se) + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, cores = chains, chains = chains,
          prior = priors,
          control = control, save_mevars = TRUE,
          file = "models/sim_dominance/h1_simple") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2")


h1_after_diagnosis <- brm(dominance ~ s(f0, by = sex) + sex + me(age, age_se) + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, cores = chains, chains = chains,
          prior = priors,
          control = control, save_mevars = TRUE,
          file = "models/sim_dominance/h1_nonlinear") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2")
marginal_smooths(h1_after_diagnosis)

h1_sex_mod_dataset_varying <- brm(dominance ~ f0 + pf + f0 * sex + me(age, age_se) + 
                                    (1 + f0 * sex || dataset), data = vcs,
          prior = priors,
          iter = iter + 2000, warmup = warmup + 1000, cores = chains, chains = chains,
          control = control, save_mevars = TRUE,
          file = "models/sim_dominance/h1_sex_mod_dataset_varying") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2")

h1_after_diagnosis_melsm <- brm(
  bf(dominance ~ s(f0, by = sex) + sex + me(age, age_se) + (1 | dataset),
     sigma ~ s(f0, by = sex) + sex + me(age, age_se) + (1 | dataset)), data = vcs,
          prior = priors,
          iter = iter + 2000, warmup = warmup + 1000, cores = chains, chains = chains,
          control = control, save_mevars = TRUE,
          file = "models/sim_dominance/h1_after_diagnosis_melsm") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2")

compare_models <- loo(h1_simple, h1_after_diagnosis, h1_sex_mod_dataset_varying,
                      h1_after_diagnosis_melsm)
compare_models
# loo_model_weights(compare_models[1:3])

sjPlot::tab_model(h1_simple, bpe = "mean",
                  terms = c("Intercept", "f0", "pf", "sex", "bsp_meageage_se"))
equiv_test <- equivalence_test(h1_simple, range = c(-0.1, 0.1))
equiv_test
```

<details><summary>Model details</summary>

```{r}
summary(h1_simple)
summary(h1_after_diagnosis)
marginal_effects(h1_after_diagnosis)
marginal_smooths(h1_after_diagnosis)
summary(h1_sex_mod_dataset_varying)
summary(h1_after_diagnosis_melsm)
```

</details>


## Hypothesis 2: 
Participants with lower voice pitch will score higher on agreeableness.

## Hypothesis 3: 
Participants with lower voice pitch will score lower on neuroticism.

## Hypothesis 4: 
Participants with lower voice pitch will report having a more unrestricted sociosexuality.

