---
title: "Preregistered analysis"
author: "Ruben Arslan"
date: "3/5/2019"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: "hide"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=F)
library(tidyverse)
library(knitr)
library(brms)
library(sjPlot)
library(bayestestR)
library(labelled)
library(cowplot)
theme_set(theme_bw())
```

## Load data

```{r}
vcs <- rio::import("data_complete_all_anonym_allZ_unfiltered.xlsx")
var_label(vcs$dominance) <- "Dominance"
var_label(vcs$neuro) <- "Neuroticism"
var_label(vcs$agree) <- "Agreeableness"
var_label(vcs$extra) <- "Extraversion"
var_label(vcs$openn) <- "Openness"
var_label(vcs$consc) <- "Conscientiousness"
var_label(vcs$soi_full) <- "Unrestricted sociosexuality"
var_label(vcs$f0) <- "Voice pitch"
var_label(vcs$pf) <- "Formants"
vcs$sex_c <- vcs$sex
vcs$sex <- factor(if_else(vcs$sex == 1, "male", "female"))
contrasts(vcs$sex) <- contr.helmert(2)
var_label(vcs$sex) <- "Sex"
set.seed(1)
var_label(vcs$age) <- "Age"
vcs <- vcs %>% 
  mutate(
    age = if_else(dataset == 9, 20, age)/10,
    age_se = if_else(dataset == 9, 3, 0.5)/10
  )
warmup <- 2000
iter <- warmup + 2000
chains <- 4
control <- list(adapt_delta = 0.99)
priors <- c(
  prior(normal(0, 3), class = b)
)

variable_labels <- c("Intercept"= "Intercept",  "sex1" = "Sex [male]", "bsp_meageage_se" = "Age±SE", "f0" = "Voice pitch (f0)", "pf" = "Formant position (Pf)", "age" = "Age")
effect_labels <- c("b_Intercept"= "Intercept",  "b_sex1" = "Sex [male]", "bsp_meageage_se" = "Age±SE", "b_f0" = "Voice pitch (f0)", "b_pf" = "Formant position (Pf)", "b_age" = "Age")

```

## Missingness patterns
```{r}
codebook::md_pattern(vcs %>% select(dominance, extra, behavior, sex, age, f0, pf, dataset))
vcs <- vcs %>% filter(!is.na(f0), !is.na(pf), !is.na(age))
```


## Neuroticism

### Visually diagnose non-linearity
```{r,warning=FALSE}
ggplot(vcs, aes(f0, neuro)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(pf, neuro)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(age*10, neuro)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  scale_x_continuous("Age") +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 
```

__Decisions upon visual diagnosis:__ 


### Models
```{r}
h0 <- brm(neuro ~ sex + age + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/neuro/h0") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

h1_simple <- brm(neuro ~ f0 + pf + sex + age + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/neuro/h1_simple") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

compare_models <- loo_compare(h0, h1_simple)
compare_models

sjPlot::tab_model(h1_simple, bpe = "mean",show.ngroups = T,ci.hyphen = ";",
                  pred.labels = variable_labels)

```

<details><summary>Model details</summary>

```{r}
summary(h1_simple)
conditional_effects(h1_simple)
# conditional_smooths(h1_after_diagnosis)
equiv_test <- equivalence_test(h1_simple, range = c(-0.1, 0.1))
equiv_test_table <- equiv_test %>% 
  mutate(Parameter = recode(Parameter, !!!effect_labels)) %>% 
  mutate(
    ROPE_Percentage = sprintf("%2.f%%", 100*ROPE_Percentage),
    HDI = sprintf("[% .2f;% .2f]", HDI_low, HDI_high)) %>% 
  select(Parameter, H0 = ROPE_Equivalence, `inside ROPE` = ROPE_Percentage, `89% HDI` = HDI)
kable(equiv_test_table, caption = "Test whether the 89% highest-density interval (HDI) is fully within the region of practical equivalence (ROPE) of [-0.1;0.1] that we set (where all continuous variables, except age are standardised).")
plot(equiv_test) + scale_y_discrete("Effect", breaks = names(effect_labels), labels = effect_labels)
```

</details>


## Openness


### Visually diagnose non-linearity
```{r,warning=FALSE}
ggplot(vcs, aes(f0, openn)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(pf, openn)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(age*10, openn)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  scale_x_continuous("Age") +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 
```

__Decisions upon visual diagnosis:__ 

### Models
```{r}
h0 <- brm(openn ~ sex + age + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/openn/h0") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

h1_simple <- brm(openn ~ f0 + pf + sex + age + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/openn/h1_simple") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

compare_models <- loo_compare(h0, h1_simple)
compare_models

sjPlot::tab_model(h1_simple, bpe = "mean",show.ngroups = T,ci.hyphen = ";",
                  pred.labels = variable_labels)

```

<details><summary>Model details</summary>

```{r}
summary(h1_simple)
conditional_effects(h1_simple)
# conditional_smooths(h1_after_diagnosis)
equiv_test <- equivalence_test(h1_simple, range = c(-0.1, 0.1))
equiv_test_table <- equiv_test %>% 
  mutate(Parameter = recode(Parameter, !!!effect_labels)) %>% 
  mutate(
    ROPE_Percentage = sprintf("%2.f%%", 100*ROPE_Percentage),
    HDI = sprintf("[% .2f;% .2f]", HDI_low, HDI_high)) %>% 
  select(Parameter, H0 = ROPE_Equivalence, `inside ROPE` = ROPE_Percentage, `89% HDI` = HDI)
kable(equiv_test_table, caption = "Test whether the 89% highest-density interval (HDI) is fully within the region of practical equivalence (ROPE) of [-0.1;0.1] that we set (where all continuous variables, except age are standardised).")
plot(equiv_test) + scale_y_discrete("Effect", breaks = names(effect_labels), labels = effect_labels)
```

</details>



## Conscientiousness

### Visually diagnose non-linearity
```{r,warning=FALSE}
ggplot(vcs, aes(f0, consc)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(pf, consc)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(age*10, consc)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  scale_x_continuous("Age") +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 
```

__Decisions upon visual diagnosis:__ 


### Models
```{r}
h0 <- brm(consc ~ sex + age + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/consc/h0") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

h1_simple <- brm(consc ~ f0 + pf + sex + age + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/consc/h1_simple") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

compare_models <- loo_compare(h0, h1_simple)
compare_models

sjPlot::tab_model(h1_simple, bpe = "mean",show.ngroups = T,ci.hyphen = ";",
                  pred.labels = variable_labels)

```

<details><summary>Model details</summary>

```{r}
summary(h1_simple)
conditional_effects(h1_simple)
# conditional_smooths(h1_after_diagnosis)
equiv_test <- equivalence_test(h1_simple, range = c(-0.1, 0.1))
equiv_test_table <- equiv_test %>% 
  mutate(Parameter = recode(Parameter, !!!effect_labels)) %>% 
  mutate(
    ROPE_Percentage = sprintf("%2.f%%", 100*ROPE_Percentage),
    HDI = sprintf("[% .2f;% .2f]", HDI_low, HDI_high)) %>% 
  select(Parameter, H0 = ROPE_Equivalence, `inside ROPE` = ROPE_Percentage, `89% HDI` = HDI)
kable(equiv_test_table, caption = "Test whether the 89% highest-density interval (HDI) is fully within the region of practical equivalence (ROPE) of [-0.1;0.1] that we set (where all continuous variables, except age are standardised).")
plot(equiv_test) + scale_y_discrete("Effect", breaks = names(effect_labels), labels = effect_labels)
```

</details>


## SOI Desire


### Visually diagnose non-linearity
```{r,warning=FALSE}
ggplot(vcs, aes(f0, desire)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(pf, desire)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(age*10, desire)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  scale_x_continuous("Age") +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 
```

__Decisions upon visual diagnosis:__ Visual diagnostic show no clear sign of nonlinearities. 
We will fit linear effects for f0, pf, and age. It is not necessary to model measurement error
in age, as dataset 9 (where age was not noted individually) is not included in these analyses.
Visually, there could be an interaction between sex and f0. 


### Models
```{r}
h0 <- brm(desire ~ sex + age + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/desire/h0") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

h1_simple <- brm(desire ~ f0 + pf + sex + age + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/desire/h1_simple") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

compare_models <- loo_compare(h0, h1_simple)
compare_models

sjPlot::tab_model(h1_simple, bpe = "mean",show.ngroups = T,ci.hyphen = ";",
                  pred.labels = variable_labels)

```

<details><summary>Model details</summary>

```{r}
summary(h1_simple)
conditional_effects(h1_simple)
# conditional_smooths(h1_after_diagnosis)
equiv_test <- equivalence_test(h1_simple, range = c(-0.1, 0.1))
equiv_test_table <- equiv_test %>% 
  mutate(Parameter = recode(Parameter, !!!effect_labels)) %>% 
  mutate(
    ROPE_Percentage = sprintf("%2.f%%", 100*ROPE_Percentage),
    HDI = sprintf("[% .2f;% .2f]", HDI_low, HDI_high)) %>% 
  select(Parameter, H0 = ROPE_Equivalence, `inside ROPE` = ROPE_Percentage, `89% HDI` = HDI)
kable(equiv_test_table, caption = "Test whether the 89% highest-density interval (HDI) is fully within the region of practical equivalence (ROPE) of [-0.1;0.1] that we set (where all continuous variables, except age are standardised).")
plot(equiv_test) + scale_y_discrete("Effect", breaks = names(effect_labels), labels = effect_labels)
```

</details>

## SOI Attitude


### Visually diagnose non-linearity
```{r,warning=FALSE}
ggplot(vcs, aes(f0, attitude)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(pf, attitude)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(age*10, attitude)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  scale_x_continuous("Age") +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 
```

__Decisions upon visual diagnosis:__ Visual diagnostic show no clear sign of nonlinearities. 
We will fit linear effects for f0, pf, and age. It is not necessary to model measurement error
in age, as dataset 9 (where age was not noted individually) is not included in these analyses.
Visually, there could be an interaction between sex and f0. 


### Models
```{r}
h0 <- brm(attitude ~ sex + age + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/attitude/h0") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

h1_simple <- brm(attitude ~ f0 + pf + sex + age + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/attitude/h1_simple") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

compare_models <- loo_compare(h0, h1_simple)
compare_models

sjPlot::tab_model(h1_simple, bpe = "mean",show.ngroups = T,ci.hyphen = ";",
                  pred.labels = variable_labels)

```

<details><summary>Model details</summary>

```{r}
summary(h1_simple)
conditional_effects(h1_simple)
# conditional_smooths(h1_after_diagnosis)
equiv_test <- equivalence_test(h1_simple, range = c(-0.1, 0.1))
equiv_test_table <- equiv_test %>% 
  mutate(Parameter = recode(Parameter, !!!effect_labels)) %>% 
  mutate(
    ROPE_Percentage = sprintf("%2.f%%", 100*ROPE_Percentage),
    HDI = sprintf("[% .2f;% .2f]", HDI_low, HDI_high)) %>% 
  select(Parameter, H0 = ROPE_Equivalence, `inside ROPE` = ROPE_Percentage, `89% HDI` = HDI)
kable(equiv_test_table, caption = "Test whether the 89% highest-density interval (HDI) is fully within the region of practical equivalence (ROPE) of [-0.1;0.1] that we set (where all continuous variables, except age are standardised).")
plot(equiv_test) + scale_y_discrete("Effect", breaks = names(effect_labels), labels = effect_labels)
```

</details>

## Sociosexuality


### Visually diagnose non-linearity
```{r,warning=FALSE}
ggplot(vcs, aes(f0, soi_full)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(pf, soi_full)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 

ggplot(vcs, aes(age*10, soi_full)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  scale_x_continuous("Age") +
  geom_smooth(method = "gam", colour = "black", formula = y ~ s(x)) +
  geom_smooth(aes(colour = sex, fill = sex), method = "gam",
              formula = y ~ s(x)) +
  scale_color_viridis_d("Sex") +
  scale_fill_viridis_d("Sex") 
```

__Decisions upon visual diagnosis:__ Visual diagnostic show no clear sign of nonlinearities. 
We will fit linear effects for f0, pf, and age. It is not necessary to model measurement error
in age, as dataset 9 (where age was not noted individually) is not included in these analyses.
Visually, there could be an interaction between sex and f0. 


### Models
```{r}
h0 <- brm(soi_full ~ sex + age + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/soi_full/h0") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

h1_simple <- brm(soi_full ~ f0 + pf + sex + age + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/soi_full/h1_simple") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

compare_models <- loo_compare(h0, h1_simple)
compare_models

sjPlot::tab_model(h1_simple, bpe = "mean",show.ngroups = T,ci.hyphen = ";",
                  pred.labels = variable_labels)

```

<details><summary>Model details</summary>

```{r}
summary(h1_simple)
conditional_effects(h1_simple)
# conditional_smooths(h1_after_diagnosis)
equiv_test <- equivalence_test(h1_simple, range = c(-0.1, 0.1))
equiv_test_table <- equiv_test %>% 
  mutate(Parameter = recode(Parameter, !!!effect_labels)) %>% 
  mutate(
    ROPE_Percentage = sprintf("%2.f%%", 100*ROPE_Percentage),
    HDI = sprintf("[% .2f;% .2f]", HDI_low, HDI_high)) %>% 
  select(Parameter, H0 = ROPE_Equivalence, `inside ROPE` = ROPE_Percentage, `89% HDI` = HDI)
kable(equiv_test_table, caption = "Test whether the 89% highest-density interval (HDI) is fully within the region of practical equivalence (ROPE) of [-0.1;0.1] that we set (where all continuous variables, except age are standardised).")
plot(equiv_test) + scale_y_discrete("Effect", breaks = names(effect_labels), labels = effect_labels)
```

</details>


## Extraversion, adjusted for dominance
```{r}
extra_adj_for_dominance <- brm(extra ~ dominance + f0 + pf + sex + me(age, age_se) + (1 | dataset), data = vcs,
          iter = iter + 1000, warmup = warmup + 1000, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/extra/extra_adj_for_dominance2") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 
extra_adj_for_dominance

dominance_adj_for_extra <- brm(dominance ~ extra  + f0 + pf + sex + age + (1 | dataset), data = vcs,
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/dominance/dominance_adj_for_extra") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 
dominance_adj_for_extra
```


## Extraversion, separate by sex
```{r}
h1_men <- brm(extra ~ f0 + pf + me(age, age_se) + (1 | dataset), data = vcs %>% filter(sex == "male"),
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/extra/h1_men") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

h1_women <- brm(extra ~ f0 + pf + me(age, age_se) + (1 | dataset), data = vcs %>% filter(sex != "male"),
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/extra/h1_women") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

h1_men
h1_women
```


## Agreeableness, separate by sex
```{r}
h1_men <- brm(agree ~ f0 + pf + me(age, age_se) + (1 | dataset), data = vcs %>% filter(sex == "male"),
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/agree/h1_men") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

h1_women <- brm(agree ~ f0 + pf + me(age, age_se) + (1 | dataset), data = vcs %>% filter(sex != "male"),
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/agree/h1_women") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

h1_men
h1_women
```


## Dominance, separate by sex
```{r}
h1_men <- brm(dominance ~ f0 + pf + age + (1 | dataset), data = vcs %>% filter(sex == "male"),
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/dominance/h1_men") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

h1_women <- brm(dominance ~ f0 + pf + age + (1 | dataset), data = vcs %>% filter(sex != "male"),
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/dominance/h1_women") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

h1_men
h1_women
```

## SOI behavior, separate by sex
```{r}
h1_men <- brm(behavior ~ f0 + pf + age + (1 | dataset), data = vcs %>% filter(sex == "male"),
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/behavior/h1_men") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

h1_women <- brm(behavior ~ f0 + pf + age + (1 | dataset), data = vcs %>% filter(sex != "male"),
          iter = iter, warmup = warmup, chains = chains, cores = chains,
          prior = priors,
          control = control, save_mevars = TRUE, 
          file = "models/behavior/h1_women") %>% 
  add_criterion("loo") %>% 
  add_criterion("bayes_R2") %>% 
  add_criterion("loo_R2") 

h1_men
h1_women
```



## Summary of results
### Models
```{r exploratoryresults,fig.width=8, fig.height=10}
openn <- readRDS("models/openn/h1_simple.rds")
neuro <- readRDS("models/neuro/h1_simple.rds")
consc <- readRDS("models/consc/h1_simple.rds")
desire <- readRDS("models/desire/h1_simple.rds")
attitude <- readRDS("models/attitude/h1_simple.rds")
soi_full <- readRDS("models/soi_full/h1_simple.rds")
theme_set(theme_cowplot())

modify <- function(outcome) {
  list(scale_y_discrete(outcome, breaks = names(effect_labels), labels = effect_labels),
  guides(fill = "none"),
  theme(panel.spacing = unit(c(0), "cm"),
        plot.margin = unit(c(0, 0.5, 0, 0.5), "cm"))
)
}
remove_x_axis <- list(
  scale_x_continuous("", limits = c(-0.5, 0.4)),
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        axis.line.x = element_blank())
)

p_extra <- plot(equivalence_test(neuro, parameters = c("b_f0", "b_pf", "b_sex1"))) + modify("Neuroticism") + remove_x_axis
p_openn <- plot(equivalence_test(openn, parameters = c("b_f0", "b_pf", "b_sex1"))) +
  modify("Openness") + remove_x_axis
p_consc <- plot(equivalence_test(consc, parameters = c("b_f0", "b_pf", "b_sex1")))  +
  modify("Conscientiousness") + remove_x_axis
p_attitude <- plot(equivalence_test(attitude, parameters = c("b_f0", "b_pf", "b_sex1"))) +
  modify("SOI attitude") + remove_x_axis
p_desire <- plot(equivalence_test(desire, parameters = c("b_f0", "b_pf", "b_sex1"))) +
  modify("SOI desire") + remove_x_axis
p_soi_full <- plot(equivalence_test(soi_full, parameters = c("b_f0", "b_pf", "b_sex1"))) +
  modify("Sociosexuality") + xlim(c(-0.5, 0.4))
legend <- get_legend(
  p_extra + 
    guides(fill = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom", legend.justification = "center")
)

neg_spacer <- -0.155
plot_grid(ncol = 1,  rel_heights = c(1, neg_spacer, 1, neg_spacer, 1,neg_spacer, 1,neg_spacer, 1, neg_spacer, 1.1, .15), align = "v", axis = "b",
          p_extra, NULL, p_openn,NULL, p_consc,NULL, p_attitude, NULL, p_desire, NULL, p_soi_full, legend)
ggsave("exploratory_rope.pdf", width = 8, height = 10)
```

### Tabular
```{r}
get_coefs <- function(model) {
model_summary <- summary(model)
nonvarying <- model_summary$fixed %>% 
  as.data.frame() %>% 
  rownames_to_column("term") %>% 
  mutate(group = "non-varying",
         outcome = as.character(model_summary$formula[[1]][[2]]))
varying <- model_summary$random %>% 
  map(~ rownames_to_column(as.data.frame(.), "term")) %>% 
  bind_rows(.id = "group") %>% 
  left_join(model_summary$ngrps %>% 
    as_tibble() %>% 
    gather(group, n), by = "group") %>% 
  mutate(#group = paste0(group, " (n=", n, ")"),
         outcome = as.character(model_summary$formula[[1]][[2]]))

two_digits <- function(x) { sprintf("%.2f", x) }
coefs <- bind_rows(nonvarying, 
                   varying)
coefs <- coefs %>% select(group, outcome, term, Estimate, `l-95% CI`, `u-95% CI`)
coefs$Estimate = two_digits(coefs$Estimate)
coefs$`l-95% CI` = two_digits(coefs$`l-95% CI`)
coefs$`u-95% CI` = two_digits(coefs$`u-95% CI`)
coefs
}

coefs <- bind_rows(get_coefs(neuro), 
                   get_coefs(openn), get_coefs(consc), get_coefs(desire),
                   get_coefs(attitude),get_coefs(soi_full))

wide_coefs <- coefs %>% 
  mutate(Estimate = paste0(Estimate, " [", `l-95% CI`, ";", `u-95% CI`, "]")) %>% 
    select(group, outcome, term, Estimate) %>% 
  mutate(term = recode(term, "meageage_se" = "Age(±SE)", "age" = "Age(±SE)"),
         outcome = fct_inorder(outcome),
         term = fct_inorder(term)) %>% 
  spread(outcome, Estimate) %>% 
  arrange(desc(group), term) %>% 
  mutate(group = fct_inorder(group))

outcome_names <- c("Neuroticism" = "neuro", "Conscientiousness" = "consc",
                   "Openness" = "openn", "Sociosexuality" = "soi_full",
                   "SOI desire" = "desire", "SOI attitude" = "attitude")

library(kableExtra)
wide_coefs %>% 
  mutate(term = str_replace_all(term, variable_labels)) %>% 
  rename(!!!syms(outcome_names), Term = term) %>% 
  select(-group) %>% 
  kable(caption = "Exploratory analysis results") %>%
  pack_rows(index = table(wide_coefs$group)) %>% 
  column_spec(column = 1, width = "3.3cm") %>% 
  column_spec(column = 2:(ncol(wide_coefs)-1), width = "3cm") %>% 
  add_header_above(c(" " = 1, "Estimated effect on each outcome [95% CI]" = ncol(wide_coefs)-2)) %>% 
  footnote("Estimated associations between outcomes, for which we had made no predictions.")
```


### Scatterplots

```{r}
outcome_names <- c("Neuroticism" = "neuro", "Conscientiousness" = "consc",
                   "Openness" = "openn", "Sociosexuality" = "soi_full",
                   "SOI desire" = "desire", "SOI attitude" = "attitude")

neuro <- ggplot(vcs, aes(f0, neuro)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(aes(colour = sex, fill = sex), method = "lm") +
  scale_color_manual("Sex", values = c("#40A5BF", "black")) +
  scale_fill_manual("Sex", values = c("#40A5BF", "black"))  +
  guides(color = F, fill = F) +
  xlab("") +
  ylab("Neuroticism") +
  theme(panel.spacing = unit(c(0), "cm"),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))

consc <- ggplot(vcs, aes(f0, consc)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(aes(colour = sex, fill = sex), method = "lm") +
  scale_color_manual("Sex", values = c("#40A5BF", "black")) +
  scale_fill_manual("Sex", values = c("#40A5BF", "black"))  +
  guides(color = F, fill = F) +
  xlab("") +
  ylab("Conscientiousness") +
  theme(panel.spacing = unit(c(0), "cm"),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))

openn <- ggplot(vcs, aes(f0, openn)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(aes(colour = sex, fill = sex), method = "lm") +
  scale_color_manual("Sex", values = c("#40A5BF", "black")) +
  scale_fill_manual("Sex", values = c("#40A5BF", "black"))  +
  guides(color = F, fill = F) +
  xlab("") +
  ylab("Openness") +
  theme(panel.spacing = unit(c(0), "cm"),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))


soi_full <- ggplot(vcs, aes(f0, soi_full)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(aes(colour = sex, fill = sex), method = "lm") +
  scale_color_manual("Sex", values = c("#40A5BF", "black")) +
  scale_fill_manual("Sex", values = c("#40A5BF", "black"))  +
  guides(color = F, fill = F) +
  xlab("") +
  ylab("Sociosexuality") +
  theme(panel.spacing = unit(c(0), "cm"),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))


desire <- ggplot(vcs, aes(f0, desire)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(aes(colour = sex, fill = sex), method = "lm") +
  scale_color_manual("Sex", values = c("#40A5BF", "black")) +
  scale_fill_manual("Sex", values = c("#40A5BF", "black"))  +
  guides(color = F, fill = F) +
  xlab("Voice pitch (f0)") +
  ylab("SOI Desire") +
  theme(panel.spacing = unit(c(0), "cm"),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))


attitude <- ggplot(vcs, aes(f0, attitude)) + 
  geom_jitter(aes(colour = sex), alpha = 0.3) +
  geom_smooth(aes(colour = sex, fill = sex), method = "lm") +
  scale_color_manual("Sex", values = c("#40A5BF", "black")) +
  scale_fill_manual("Sex", values = c("#40A5BF", "black"))  +
  guides(color = F, fill = F) +
  xlab("Voice pitch (f0)") +
  ylab("SOI Attitude") +
  theme(panel.spacing = unit(c(0), "cm"),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))

plot_grid(ncol = 2,  openn, neuro, consc, soi_full, attitude, desire,
          align = "hv")
ggsave("scatterplots_exploratory.pdf", width = 8, height = 8)
```

