---
title: "Do voices carry valid information about a speaker’s personality?"
author: "Julia Stern, Christoph Schild, Benedict C. Jones, Lisa M. DeBruine, Amanda Hahn, David A. Puts, Ingo Zettler, Tobias L. Kordsmeyer, David Feinberg, Dan Zamfir, Lars Penke, & Ruben C. Arslan"
date: "4/10/2021"
output: html_document
---

## Results

- [Integration/Aggregation](0_aggregate_pomp.html) of individual datasets.
- [Codebook](1_codebook.html):  The codebook contains metadata, means, missingness, correlations, sex differences, age trends, and further information on all variables in the study. We also provide a [codebook with unstandardised variables](1_codebook_before_standardisation.html).
- [Preregistered tests](2_preregistered_tests.html) for preregistered outcomes (dominance, extraversion, agreeableness, SOI behavior)
- [Exploratory analyses](3_exploratory_analyses.html) for additional outcomes.
- [Robustness checks](4_robustness_checks.html) for the preregistered outcomes.

```{r setup,echo=F}
library(r2d3)
```


## Voice pitch and formants
```{r echo=F,message=F}
library(tidyverse)
author_voices <- rio::import("author_voices/acoustics-all.xlsx")
vcs <- rio::import("data_complete_2021_unstd_pomp.rds")

author_voices <- author_voices %>%
  mutate(f0 = (`Mean F0` - mean(vcs$f0,na.rm=T))/sd(vcs$f0,na.rm=T),
         f1 = (f1 - mean(vcs$f1,na.rm=T))/sd(vcs$f1,na.rm=T),
         f2 = (f2 - mean(vcs$f2,na.rm=T))/sd(vcs$f2,na.rm=T),
         f3 = (f3 - mean(vcs$f3,na.rm=T))/sd(vcs$f3,na.rm=T),
         f4 = (f4 - mean(vcs$f4,na.rm=T))/sd(vcs$f4,na.rm=T),
         pf = (f1+f2+f3+f4)/4,
         pf = (pf - mean(vcs$pf,na.rm=T))/sd(vcs$pf,na.rm=T),
         author = recode(Filename, "Lars" = "LP",
                         "DaveF" = "DF",
                         "DaveP" = "DAP",
                         "Christoph" = "CS",
                         "Ruben" = "RCA",
                         "Julia" = "JS",
                         "Amanda" = "AH",
                         "Ingo" = "IZ",
                         "Lars" = "LP",
                         "Tobi" = "TLK"),
         Filename = paste0(Filename, ".wav"),
        pf_pos = pf + case_when(author == "RCA" ~ 0,
                                author == "CS" ~ 0,
                                TRUE ~ 0))

 # for(i in 1:nrow(author_voices)) {
 #   av::av_audio_convert(paste0("author_voices/", author_voices$Filename[i], ".wav"),
 #                        paste0("author_voices/", author_voices$author[i], ".mp3"))
 # }
```

To hear different voice pitches and formants, click the initials of the authors of our study below. You'll hear each of us speak the letters "A-E-I-O-U". The big, clickable dots show the authors; they are superimposed on the data used in this study (men coloured in black, women coloured in blue).

```{r echo=F}
vcs <- rio::import("data_complete_2021_zscored_no_outliers.rds")
vcs$sex <- vcs$sex_c

data <- vcs %>% 
  # mutate(f0 = scale(f0), pf = scale(pf)) %>%
  full_join(author_voices %>% mutate(voice_id=1e5+row_number()), suffix = c("_vcs", ""), by = "voice_id")

data$x <- data$f0
data$y <- data$pf

options <- list(margin = 50,
               barPadding = 0.1,
               colour = "rgba(0,0,0,1)",
               hovercolour = "orange",
               xLabel = "Voice pitch (f0)",
               yLabel = "Formants (pf)",
               xmin = min(data$x, data$f0_vcs, na.rm = T),
               xmax = max(data$x, data$f0_vcs, na.rm = T),
               ymin = min(data$y, data$pf_vcs, na.rm = T),
               ymax = max(data$y, data$pf_vcs, na.rm = T),
               chartTitle = "Voices"
     )
```

```{r echo=F, fig.width=9.7,fig.height=5}
r2d3(data=data, options = options, script = "d3_scatterplot.js")
```


### Reproducibility
This repository uses the [renv](https://rstudio.github.io/renv/) package to make
it easier to rerun analyses using the same setup and package versions that were
used to create them.

<details><summary>Here's a classical session info.</summary>

```{r}
library(tidyverse)
library(knitr)
library(brms)
library(sjPlot)
library(bayestestR)
library(labelled)
library(cowplot)
library(labelled)
library(codebook)
library(ggstatsplot)
sessionInfo()
```

</details>

<details><summary>Here's our renv lockfile.</summary>

```{r}
cat(readLines("renv.lock"), sep = "\n")
```
</details>

