---
title: "Do voices carry valid information about a speaker’s personality?"
author: "Julia Stern, Christoph Schild, Benedict C. Jones, Lisa M. DeBruine, Amanda Hahn, David A. Puts, Ingo Zettler, Tobias L. Kordsmeyer, David Feinberg, Dan Zamfir, Lars Penke, & Ruben C. Arslan"
date: "2/7/2020"
output: html_document
---


## Results

- [Codebook](1_codebook.html):  The codebook contains metadata, means, missingness, correlations, sex differences, age trends, and further information on all variables in the study. We also provide a [codebook with unstandardised variables](1_codebook_before_standardisation.html).
- [Preregistered tests](2_preregistered_tests.html)
- [Exploratory analyses and robustness checks](3_exploratory_analyses.html)

```{r setup,echo=F}
library(r2d3)
```


## Voice pitch and formants
```{r echo=F,message=F}
library(tidyverse)
author_voices <- readxl::read_excel("author_voices/measures.xlsx")
vcs <- readxl::read_excel("data_complete_all_anonym_PfZ.xlsx")# %>% filter(dataset==1 | dataset == 10)
# vcs2 <- rio::import("data_complete_all_anonym_allZ_unfiltered.xlsx")
# vcs <- vcs %>% left_join(vcs2, by = "voice_id")
# cor.test(vcs$extra.x, vcs$extra.y)
# cor.test(vcs$dominance.x, vcs$dominance.y)
# cor.test(vcs$f0.x, vcs$f0.y)
# cor.test(vcs$f1.x, vcs$f1.y)
# cor.test(vcs$pf.x, vcs$pf.y)
# psych::describe(vcs$f1)

vcs <- vcs %>% filter(dataset != 10, dataset != 2, dataset != 3)

# psych::describe(vcs$f1)

vcs <- vcs %>% mutate(pf = (scale(f1)+scale(f2)+scale(f3)+scale(f4))/4)

# vcs <- vcs %>% mutate(pf=scale(pf))

# median(vcs$pf,na.rm=T) + 2* mad(vcs$pf,na.rm=T)
# median(vcs$f0,na.rm=T) + 2* mad(vcs$f0,na.rm=T)
# qplot(vcs$f0)
# vcs %>% filter(pf > (median(vcs$pf,na.rm=T) + 2* mad(vcs$pf,na.rm=T))) %>% select(dataset, pf, f0, sex)

author_voices <- author_voices %>%
  mutate(f0 = (`Mean F0` - mean(vcs$f0,na.rm=T))/sd(vcs$f0,na.rm=T),
         f1 = (f1 - mean(vcs$f1,na.rm=T))/sd(vcs$f1,na.rm=T),
         f2 = (f2 - mean(vcs$f2,na.rm=T))/sd(vcs$f2,na.rm=T),
         f3 = (f3 - mean(vcs$f3,na.rm=T))/sd(vcs$f3,na.rm=T),
         f4 = (f4 - mean(vcs$f4,na.rm=T))/sd(vcs$f4,na.rm=T),
         pf = (f1+f2+f3+f4)/4,
         # pf = (pf - mean(vcs$pf,na.rm=T))/sd(vcs$pf,na.rm=T),
         author = recode(Filename, "Lars.wav" = "LP",
                         "Davef" = "DAP",
                         "christoph" = "CS",
                         "ruben" = "RCA",
                         "Julia" = "JS",
                         "amanda.wav" = "AH"),
        pf_pos = pf + case_when(author == "RCA" ~ -0.05,
                                author == "CS" ~ +0.05,
                                TRUE ~ 0))
# 
#  for(i in 1:nrow(author_voices)) {
#    av::av_audio_convert(paste0("author_voices/", author_voices$Filename[i]), 
#                         paste0("author_voices/", author_voices$author[i], ".mp3"))
#  }
```

To hear different voice pitches and formants, click the initials of the authors of our study below. You'll hear each of us speak the letters "A-E-I-O-U". The big, clickable dots show the authors; they are superimposed on the data used in this study (men coloured in black, women coloured in blue).

```{r echo=F}
options = list(margin = 50,
               barPadding = 0.1,
               colour = "rgba(255,0,0,1)",
               hovercolour = "rgba(50,50,50,1)",
               xLabel = "x label",
               yLabel = "y label",
               xmin = max(author_voices$f0),
               xmax = max(author_voices$f0),
               ymin = min(author_voices$pf),
               ymax = max(author_voices$pf),
               chartTitle = "Chart Title"
     )
data <- vcs %>% mutate(f0 = scale(f0)) %>% full_join(author_voices %>% mutate(voice_id=1e5+row_number()), suffix = c("_vcs", ""), by = "voice_id")
data$x <- data$f0
data$y <- data$pf

options <- list(margin = 50,
               barPadding = 0.1,
               colour = "rgba(0,0,0,1)",
               hovercolour = "orange",
               xLabel = "Voice pitch (f0)",
               yLabel = "Formants (pf)",
               xmin = min(data$x, data$f0_vcs, na.rm = T),
               xmax = max(data$x, data$f0_vcs, na.rm = T),
               ymin = min(data$y, data$pf_vcs, na.rm = T),
               ymax = max(data$y, data$pf_vcs, na.rm = T),
               chartTitle = "Voices"
     )
```

```{r echo=F, fig.width=9.7,fig.height=5}
r2d3(data=data, options = options, script = "d3_scatterplot.js")
```


### Reproducibility
This repository uses the [renv](https://rstudio.github.io/renv/) package to make
it easier to rerun analyses using the same setup and package versions that were
used to create them.

<details><summary>Here's a classical session info.</summary>

```{r}
# library(tidyverse)
# library(knitr)
# library(brms)
# library(sjPlot)
# library(bayestestR)
# library(labelled)
# library(cowplot)
# library(labelled)
# library(codebook)
# library(ggstatsplot)
# sessionInfo()
```

</details>

<details><summary>Here's our renv lockfile.</summary>

```{r}
cat(readLines("renv.lock"), sep = "\n")
```
</details>


```{r}
# library(rPraat)
# library(tidyverse)
# library(dygraphs)
# wav <- snd.read("author_voices/RCA.mp3")
# snd.plot(wav) %>% dyAxis("y", label = "Amplitude")
# pt <- as.pitch(wav)
# 
# pt.plot(as.pt(wav))
# pitch.plot(pt, scaleIntensity = TRUE, showStrength = TRUE)
# 
# wav <- snd.read("author_voices/RCA.mp3")
# 
# soundgen::analyze("author_voices/ruben.wav", samplingRate = 16000, priorSD = 24, 
#             pitchMethods = c('autocor', 'cep', 'dom', 'spec', 'hps'),
#             plot = TRUE, ylim = c(0, 4))
```

