---
title: "Do voices carry valid information about a speaker’s personality?"
author: "Julia Stern, Christoph Schild, Benedict C. Jones, Lisa M. DeBruine, Amanda Hahn, David A. Puts, Ingo Zettler, Tobias L. Kordsmeyer, David Feinberg, Dan Zamfir, Lars Penke, & Ruben C. Arslan"
date: "2/7/2020"
output: html_document
---


## Results

- [Codebook](1_codebook.html):  The codebook contains metadata, means, missingness, correlations, sex differences, age trends, and further information on all variables in the study.
- [Preregistered tests](2_preregistered_tests.html)
- [Exploratory analyses and robustness checks](3_exploratory_analyses.html)


### Reproducibility
This repository uses the [renv](https://rstudio.github.io/renv/) package to make
it easier to rerun analyses using the same setup and package versions that were
used to create them.

<details><summary>Here's a classical session info.</summary>

```{r}
library(tidyverse)
library(knitr)
library(brms)
library(sjPlot)
library(bayestestR)
library(labelled)
library(cowplot)
library(labelled)
library(codebook)
library(ggstatsplot)
sessionInfo()
```

</details>

<details><summary>Here's our renv lockfile.</summary>

```{r}
cat(readLines("renv.lock"), sep = "\n")
```
</details>
